### 2017-02-24 manuscript/manuscript.tex
Initial outlines.

%% bare_conf.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE!
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[10pt, conference, compsocconf]{IEEEtran}
% Add the compsocconf option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

\usepackage{graphicx}
% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath,amssymb}
%\usepackage{amsmath,amssymb}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
\usepackage{algorithmic,listings, subfigure}
\lstset{language=C,basicstyle=\small\ttfamily, basewidth=0.51em}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

%\usepackage{mdwmath}
%\usepackage{mdwtab}
% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
% especially mdwmath.sty and mdwtab.sty which are used to format equations
% and tables, respectively. The MDWtools set is already installed on most
% LaTeX systems. The lastest version and documentation is available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

%\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** SUBFIGURE PACKAGES ***
%\usepackage[tight,footnotesize]{subfigure}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.

%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\usepackage[caption=false,font=footnotesize]{subfig}
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Documentation is contained in the stfloats.sty comments as well as in the
% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
% does not allow \baselineskip to stretch. Authors submitting work to the
% IEEE should note that IEEE rarely uses double column equations and
% that authors should try to avoid such use. Do not be tempted to use the
% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
% not format its papers in such ways.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% Read the url.sty source comments for usage information. Basically,
% \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\usepackage{url}
\usepackage{tabularx}
\usepackage{subfig}

\graphicspath{{figures/}}
\pagestyle{plain}
\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Application-Level Regression Testing Framework using Jenkins}

% author names and affiliations
% use a multiple column layout for up to two different
% affiliations

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
%
\author{\IEEEauthorblockN{Author1, Author2, Author3}
%xxxx\IEEEauthorrefmark{3} and
%xxxx\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}National Institute for Computational Science\\
National Institute for Computational Sciences\\
The University of Tennessee, Knoxville, TN 37996\\
\{email1,email2,email3\}@domain.edu}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Electrical Engineering and Computer Science Department\\University of Tennessee, Knoxville, TN 37996\\xx@eecs.utk.edu}
%}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle
\thispagestyle{plain}

\begin{abstract}
This paper will explore the challenges of regression testing and monitoring of large scale systems such as NCSA’s Blue Waters. Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance. Another requirement was to find an automated solution for running a suite of test jobs that reveal the system health after upgrades and outages before returning the system to service. We evaluated test frameworks such as Inca [1] and Jenkins [2]. Jenkins was chosen for its versatility, large user base, and multitudes of plugins including plotting test results over time. We utilize these plots to track trends and alert us to system-level issues before they are reported by our partners (users). Not only does Jenkins have the ability to store historical data but it can also send customized notifications (e.g. send email or text pages) based on the result of a test. Some of the requirements we had include two-factor authentication to access Jenkins GUI with privileges to execute tests and account management through LDAP. In this paper we describe our implementation of these requirements to ensure a secure and usable deployment of a Jenkins instance.

Our Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. Security was of the highest concern since Jenkins has the ability to execute commands on our login nodes. Jenkins is set to log in as a standard user account with passwordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. The VM (bwjenkins) was closely vetted by our security team on our test and development system (TDS) before it was allowed access to Blue Waters. Iptables was used to lock bwjenkins down to a small internal ip space to ensure the highest security. An anonymous user account was enabled with ‘read-only’ access to view current and historical test results. During a test, Jenkins downloads software, builds the software, submits a job, awaits completion, gathers and plots the results or returns error information during a failure. These are full end to end functionality testing of the programming environment, queueing system, license servers and provide historical metrics to quickly detect regressions.

In this paper we describe in detail our challenges and experiences in deploying Jenkins as a user-level system-wide regression testing and monitoring framework for Blue Waters. We will also show some application-based system-level tests we have implemented in Jenkins and share results of those tests. The deployment of Jenkins allow us to monitor and detect issues as early as possible from the perspective of a user on Blue Waters, eventually providing a more efficient service for better user experience.
\end{abstract}

\begin{IEEEkeywords}
Performance; Benchmarking; Computer architecture
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Motivation}

\section{Jenkins Configuration}
\label{sec:JenkinsConfiguration}

\subsection{Introduction to Jenkins}
\subsection{Master-Node Configuration}
\subsection{Accessing Login Nodes}

\section{Authentication and Authorization}
\label{sec:AuthenticationAuthorization}

\subsection{Security Considerations}
\subsection{Configuration Choices}

\section{Anatomy of A Test}
\label{sec:TestAnatomy}

\section{SWTools Integration}
\label{sec:SWToolsIntegration}

\section{Use Cases}
\label{sec:results}

\section{Conclusion}
\label{sec:conclusion}

% use section* for acknowledgement
\section*{Acknowledgment}
This research used resources at the National Institute for Computational Sciences, funded by the National Science Foundation (NSF).

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
\IEEEtriggercmd{\enlargethispage{-2in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)

%\begin{thebibliography}{9}

%\bibliographystyle{IEEEtran}
%\bibliographystyle{unsrt}
%\bibliography{references}

%\end{thebibliography}

% that's all folks
\end{document}

### 2017-02-28 manuscript/manuscript.tex
Cleaned up comments.
Example figure and listing in paper.

@@
-%% bare_conf.tex
-%% V1.3
-%% 2007/01/11
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE!
-%% User assumes all risk.
-%% In no event shall IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%
-%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices can trigger bugs that do  ***
-% *** not appear when using other class files.                            ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-% Note that the a4paper option is mainly intended so that authors in
-% countries using A4 can easily print to A4 and see how their papers will
-% look in print - the typesetting of the document will not typically be
-% affected with changes in paper size (but the bottom and side margins will).
-% Use the testflow package mentioned above to verify correct handling of
-% both paper sizes by the user's LaTeX system.
-%
-% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
-% should be used if it is desired that the figures are to be displayed in
-% draft mode.
-%
 \documentclass[10pt, conference, compsocconf]{IEEEtran}
-% Add the compsocconf option for Computer Society conferences.
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
-% not currently provide for hyperlinked citations.
-% The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
-% The documentation is contained in the cite.sty file itself.
 
 \usepackage{graphicx}
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
-% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-%\usepackage[cmex10]{amsmath,amssymb}
-%\usepackage{amsmath,amssymb}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics. If using
-% it, be sure to load this package with the cmex10 option to ensure that
-% only type 1 fonts will utilized at all point sizes. Without this option,
-% it is possible that some math symbols, particularly those within
-% footnotes, will be rendered in bitmap form which will result in a
-% document that can not be IEEE Xplore compliant!
-%
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-\usepackage{algorithmic,listings, subfigure}
+\usepackage{algorithmic,listings}
 \lstset{language=C,basicstyle=\small\ttfamily, basewidth=0.51em}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
-% There is also a support site at:
-% http://algorithms.berlios.de/index.html
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/tools/
-
-%\usepackage{mdwmath}
-%\usepackage{mdwtab}
-% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
-% especially mdwmath.sty and mdwtab.sty which are used to format equations
-% and tables, respectively. The MDWtools set is already installed on most
-% LaTeX systems. The lastest version and documentation is available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-%\usepackage{eqparbox}
-% Also of notable interest is Scott Pakin's eqparbox package for creating
-% (automatically sized) equal width boxes - aka "natural width parboxes".
-% Available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/
-
-% *** SUBFIGURE PACKAGES ***
-%\usepackage[tight,footnotesize]{subfigure}
-% subfigure.sty was written by Steven Douglas Cochran. This package makes it
-% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
-% work, it is a good idea to load it with the tight package option to reduce
-% the amount of white space around the subfigures. subfigure.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at:
-% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
-% subfigure.sty has been superceeded by subfig.sty.
-
-%\usepackage[caption=false]{caption}
-%\usepackage[font=footnotesize]{subfig}
-% subfig.sty, also written by Steven Douglas Cochran, is the modern
-% replacement for subfigure.sty. However, subfig.sty requires and
-% automatically loads Axel Sommerfeldt's caption.sty which will override
-% IEEEtran.cls handling of captions and this will result in nonIEEE style
-% figure/table captions. To prevent this problem, be sure and preload
-% caption.sty with its "caption=false" package option. This is will preserve
-% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later
-% (recommended due to many improvements over 1.2) of subfig.sty supports
-% the caption=false option directly:
-%\usepackage[caption=false,font=footnotesize]{subfig}
-%
-% The latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
-% The latest version and documentation of caption.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure. The latest version and documentation can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/base/
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
-% Documentation is contained in the stfloats.sty comments as well as in the
-% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
-% does not allow \baselineskip to stretch. Authors submitting work to the
-% IEEE should note that IEEE rarely uses double column equations and
-% that authors should try to avoid such use. Do not be tempted to use the
-% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
-% not format its papers in such ways.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
-% Read the url.sty source comments for usage information. Basically,
-% \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
 \usepackage{url}
@@
 \usepackage{subfig}
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
 
@@
 \begin{document}
-%
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
+
 \title{Application-Level Regression Testing Framework using Jenkins}
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{example}
+\caption{This is an example figure with its caption.}
+\label{fig:example}
+\end{figure}
+
+\begin{lstlisting}[float,frame=tb,captionpos=t,language=bash,caption={Apache Configuration Example}, label=lst:apacheconfig]
+
+# First, we configure the "default" to be a very 
+# restrictive set of features.  
+#
+<Directory />
+    Options FollowSymLinks
+    AllowOverride None  
+</Directory>
+
+\end{lstlisting}
+
 \section{Jenkins Configuration}

### 2017-03-01 manuscript.tex
Add files via upload
added section on filesystem tests

--- 2017-02-28 manuscript/manuscript.tex
@@
 %
-\author{\IEEEauthorblockN{Author1, Author2, Author3}
+\author{\IEEEauthorblockN{Author1, Author2, Galen Arnold}
 %xxxx\IEEEauthorrefmark{3} and
@@
 \label{sec:results}
+\begin{filesytem tests}
+We created Jenkins tests to run the IOR MPI parallel filesystem test to run at a modest scale and validate filesystem functionality and performance for the scratch filesystem on a periodic basis.
+The mdtest metadata test is also run on the home and scratch filesystems to validate metadata server performance.
+Both tests create plots that we review when checking recent overall filesystem performance.
+These user-facing tests complement the fine-grained detail we are able to glean from the backed system-side counters in our OVIS database where we record details about individual server metrics and network traffic on the Cray Gemini fabric.
+Both of the tests are set to run as scheduled by Jenkins with a best-effort through our batch system.
+The tests block such that the next test will not start until the previous one has completed through the batch system.
+We employ a watchdog script to block the exit from the test until the batch system marks it as finished.
+\end{filesystem tests}
 

### 2017-03-01 manuscript/manuscript.tex
Update manuscript.tex
testing update of author2 and email address.
Update manuscript.tex
test , added myself to author list

@@
 %
-\author{\IEEEauthorblockN{Author1, Author2, Author3}
+\author{\IEEEauthorblockN{Author1, Timothy Bouvet, Galen Arnold}
 %xxxx\IEEEauthorrefmark{3} and
@@
 The University of Tennessee, Knoxville, TN 37996\\
-\{email1,email2,email3\}@domain.edu}
+\{email1,tbouvet@illinois.edu,email3\}@domain.edu}
 %\IEEEauthorblockA{\IEEEauthorrefmark{4}Electrical Engineering and Computer Science Department\\University of Tennessee, Knoxville, TN 37996\\xx@eecs.utk.edu}

### 2017-03-01 manuscript/manuscript.tex

@@
 \label{sec:results}
-\begin{filesytem tests}
+\subsection{filesystem tests}
 We created Jenkins tests to run the IOR MPI parallel filesystem test to run at a modest scale and validate filesystem functionality and performance for the scratch filesystem on a periodic basis.
@@
 We employ a watchdog script to block the exit from the test until the batch system marks it as finished.
-\end{filesystem tests}
 

### 2017-03-01 manuscript/manuscript.tex
Add files via upload

@@
 \usepackage{subfig}
+\usepackage{float}
 % correct bad hyphenation here
@@
 \label{sec:results}
-\subsection{filesystem tests}
+\subsection{IOR Lustre scratch test}
+We created Jenkins tests to run the IOR MPI parallel filesystem test to run at a modest scale and validate filesystem functionality and performance for the scratch filesystem on a periodic basis.
+One of our best practices is to provide a management level summary description for casual jenkins users who want to view the test but do not need to understand the jenkins configuration and execution details.
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.5\textwidth]{IOR-bluewaters-descr}
+\caption{ IOR description in jenkins }
+\label{fig:IOR-bluewaters-descr}
+\end{figure}
+Where possible, tests build from source and exercise multiple user-facing system components such as: git for external connectivity and loading modules to test the defaults in the environment.
+Where scripts on the SSH site are used, they are echoed and/or displayed with "cat -n" to make console output verbose and easy to debug in case of errors.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{IOR-configuration-sample}
+\caption{ IOR configuration sample }
+\label{fig:IOR-configuration-sample}
+\end{figure}
+
+The test is set to run as scheduled by Jenkins with a best-effort through our batch system.
+The test blocks such that the next test will not start until the previous one has completed.
+We employ a watchdog script to block the exit from the test until the batch system marks it as finished.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{IOR-watchdog-out}
+\caption{ IOR watchdog console output }
+\label{fig:IOR-watchdog-out}
+\end{figure}
+For tests that produce an interesting performance metric like IOR, we save that output to a file and use the Jenkins plotting feature to produce plots. 
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{IOR-plot}
+\caption{ IOR plot view }
+\label{fig:IOR-plot}
+\end{figure}
+A plot like this helps us with performance baselines and we can quickly react to changes in the software environment or filesystem configuration.
+
+\subsection{mdtest Lustre tests}
 We created Jenkins tests to run the IOR MPI parallel filesystem test to run at a modest scale and validate filesystem functionality and performance for the scratch filesystem on a periodic basis.

### 2017-03-01 manuscript/manuscript.tex
mdtest subsection draft
added screenshots and draft text to the mdtest subsection

@@
 We created Jenkins tests to run the IOR MPI parallel filesystem test to run at a modest scale and validate filesystem functionality and performance for the scratch filesystem on a periodic basis.
+The test is scaled to provide representative performance numbers for a typical small application while not creating issues with other jobs or the filesystem at large.
 One of our best practices is to provide a management level summary description for casual jenkins users who want to view the test but do not need to understand the jenkins configuration and execution details.
-\begin{figure}[h!]
+\begin{figure}[H]
 \centering
@@
 \subsection{mdtest Lustre tests}
-We created Jenkins tests to run the IOR MPI parallel filesystem test to run at a modest scale and validate filesystem functionality and performance for the scratch filesystem on a periodic basis.
-The mdtest metadata test is also run on the home and scratch filesystems to validate metadata server performance.
-Both tests create plots that we review when checking recent overall filesystem performance.
-These user-facing tests complement the fine-grained detail we are able to glean from the backed system-side counters in our OVIS database where we record details about individual server metrics and network traffic on the Cray Gemini fabric.
-Both of the tests are set to run as scheduled by Jenkins with a best-effort through our batch system.
-The tests block such that the next test will not start until the previous one has completed through the batch system.
-We employ a watchdog script to block the exit from the test until the batch system marks it as finished.
+The mdtest metadata test is run on the home and scratch filesystems to validate metadata server performance.
+The IOR and mdtest user-facing tests complement the fine-grained detail we are able to glean from the backed system-side counters in our OVIS database where we record details about individual server metrics and network traffic on the Cray Gemini fabric.
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{mdtest-plot}
+\caption{ mdtest plot view }
+\label{fig:mdtest-plot}
+\end{figure}
+
+An additional best practice is to enable E-mail Notifications to the test author and/or other interested parties.
+E-mail for unstable builds will cause an E-mail every time the test state changes (from successful to failing and again when back to successful ).
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{mdtest-config-email}
+\caption{ mdtest email configuration }
+\label{fig:mdtest-config-email}
+\end{figure}
 

### 2017-03-02 manuscript/manuscript.tex
cleaned up typo

@@
 The University of Tennessee, Knoxville, TN 37996\\
-\{email1,tbouvet@illinois.edu,email3\}@domain.edu}
+\{email1,tbouvet@illinois.edu,gwarnold@illinois.edu\}@domain.edu}
 %\IEEEauthorblockA{\IEEEauthorrefmark{4}Electrical Engineering and Computer Science Department\\University of Tennessee, Knoxville, TN 37996\\xx@eecs.utk.edu}
@@
 \section{Motivation}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{example}
-\caption{This is an example figure with its caption.}
-\label{fig:example}
-\end{figure}
 
@@
 
+\begin{lstlisting}[float,frame=tb,captionpos=t,language=bash,caption={pbs/torque watchdog script}, label=lst:watchdog]
+#!/bin/bash
+echo "=== RUNNING $0 ==="
+if [ $# -lt 1 ]
+then
+  echo "$0: missing argument for jobid"
+  exit 1
+fi
+while true
+do
+	MYQSTAT=`qstat $1`
+	if test "$MYQSTAT" = ""
+        then
+		echo $1 finished
+		exit
+	else
+		DATE=`date`
+		echo "$DATE: waiting for $1 to finish"
+	fi
+	sleep 5m
+done
+\end{lstlisting}
+
 \begin{figure}[H]
@@
 \label{fig:mdtest-config-email}
+\end{figure}
+
+\subsection{special projects}
+The tabs display of our Jenkins instance is used to group tests and we add tabs for special projects.
+For example we clone existing tests for evaluating a new software stack on our test login node.
+Our test rack has a separate set of tests from our production system and is used as our Jenkins test development area.
+The sustained petascale performance benchmarks are in their own tab since they can run at scale and are only run on-demand (not scheduled by Jenkins ).
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{tabs-display}
+\caption{ tabs for project areas }
+\label{fig:tabs-display}
 \end{figure}

### 2017-03-02 manuscript/manuscript.tex
update my copy

--- 2017-03-01 manuscript/manuscript.tex
@@
 \usepackage{float}
+\usepackage{underscore}
 % correct bad hyphenation here
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{example}
-\caption{This is an example figure with its caption.}
-\label{fig:example}
-\end{figure}
-
 \begin{lstlisting}[float,frame=tb,captionpos=t,language=bash,caption={Apache Configuration Example}, label=lst:apacheconfig]
@@
 \subsection{Security Considerations}
+Blue Waters is an OTP only restricted access system.
+Enabling Jenkins access to Blue Waters posed some unique security hurdles that we had to overcome.
+Jenkins has the ability to execute commands on our login nodes.
+Jenkins is set to log in as a standard user account with passwordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM.
+We restricting access to the physical VM and Jenkins GUI (bwjenkins) utilizing iptables, SSL and OTP.
+The VM allows restricted host-based ssh (port 22) access from two secure OTP only administrative systems.
+The Jenkins GUI presented additional challenges.
+We setup reverse proxy to run Jenkins behind apache/http with SSL for access to the administrative console.
+All the configuration is in /etc/httpd/config.d/ssl.conf.
+An anonymous GUI view was setup (config file snippets below)
+
+\begin{lstlisting}
+/etc/ssh/sshd_config:
+Match Host bwbh1.ncsa.illinois.edu,
+bwbh2.ncsa.illinois.edu
+HostbasedAuthentication yes
+
+/etc/sysconfig/iptables:
+-A INPUT -s 141.142.0.0/16 -m state --state NEW -m tcp 
+-p tcp --dport 22 -j ACCEPT
+-A INPUT -s 172.16.0.0/15 -m state --state NEW -m tcp 
+-p tcp --dport 22 -j ACCEPT *delete maybe*
+-A INPUT  -m state --state NEW -m tcp -p tcp --dport 80 
+-j ACCEPT
+-A INPUT -s 141.142.0.0/16 -m state --state NEW -m tcp 
+-p tcp --dport 443 -j ACCEPT
+
+/etc/httpd/config.d/ssl.conf:
+Listen 443
+<VirtualHost _default_:443>
+SSLSessionCache         shmcb:/var/cache/mod_ssl/scache
+(512000) Reuben how you cache the opt?
+SSLSessionCacheTimeout  300
+ServerName bwjenkins.ncsa.illinois.edu:443
+ # -- The following sets ReverseProxy for Jenkins
+  ProxyRequests       Off
+  ProxyPreserveHost   On
+  AllowEncodedSlashes On
+  <Proxy *>
+    Order deny,allow
+    Allow from all
+  </Proxy>
+  ProxyPass       / http://localhost:8080/ nocanon
+  ProxyPassReverse / http://localhost:8080/
+  ProxyPassReverse / http://bwjenkins.ncsa.illinois.edu/
+  RequestHeader set X-Forwarded-Proto "https"
+  RequestHeader set X-Forwarded-Port "443"
+
+  DefineExternalAuth pwauth+session pipe /usr/local/bin/
+  pwauth+session
+  <LocationMatch / > 
+    AuthType Basic
+    AuthBasicProvider external
+    AuthName "NCSA RSA OTP login" 
+    AuthExternal pwauth+session
+    require valid-user
+
+    RequestHeader unset "X-Forwarded-User"
+    RequestHeader set "X-Forwarded-User" (REMOTE_USER)
+
+  </LocationMatch>
+\end{lstlisting}
+
 \subsection{Configuration Choices}

### 2017-03-02 manuscript/manuscript.tex
added some space for next page
added filesystem dashboard
wiki filesystem dashboard use case

@@
 SSLSessionCache         shmcb:/var/cache/mod_ssl/scache
-(512000) Reuben how you cache the opt?
 SSLSessionCacheTimeout  300
@@
 
+\subsection{filesystem dashboard}
+Our Jenkins instance is a source of information for a filesystem dashboard display we maintain in our wiki.
+The http:// urls for the plot images are shown on the dashboard and provide a recent-time display of filesystem metrics from a user point of view.
+We add a Jenkins test to track the response time of /bin/ls on the login nodes--a reasonable metric of metadata server health and also the number one issue reported by users when we are having filesystem issues.
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{wiki-dashboard}
+\caption{ filesystem dashboard displaying multiple Jenkins plots }
+\label{fig:wiki-dashboard}
+\end{figure}
+
 \subsection{special projects}

### 2017-03-02 manuscript/manuscript.tex
cleaned up security section

@@
 Security was of the highest concern since Jenkins has the ability to execute commands on our login nodes.
-Jenkins is set to log in as a standard user account with passwordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM.
+Jenkins is set to log in as a standard user account with pass-wordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM.
 The VM (bwjenkins) was closely vetted by our security team on our test and development system (TDS) before it was allowed access to Blue Waters.
@@
 \subsection{Security Considerations}
+Enabling Jenkins access to Blue Waters posed some unique security hurdles that we had to overcome.
 Blue Waters is an OTP only restricted access system.
-Enabling Jenkins access to Blue Waters posed some unique security hurdles that we had to overcome.
-Jenkins has the ability to execute commands on our login nodes.
-Jenkins is set to log in as a standard user account with passwordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM.
+Jenkins has the ability to execute user-level commands on our login nodes.
+Jenkins has some unfortunate default settings.
+The access control is set to "Jenkins' own user database," and the "Allow users to sign up" option is enabled, so if you don't have an account, you can create one by providing your name, e-mail and a password.
+Additionally, there's an authorization option enabled which says "Logged-in users can do anything." So, once you complete the sign up form, you have full admin access to the system.
+This required us initially to test the deployment with our test and development (TDS) CRAY.
+This resulted in the following requirements.
+Restricted OTP access to the physical system that will host Jenkins.
+In addition, OTP only access to the Jenkins GUI command console that must be contained within our IP space.
+The Jenkins GUI will also restrict the command console access to our Blue Waters LDAP server.
+
+\subsection{Configuration Choices}
+Jenkins instance was deployed on a vSphere managed VM running Centos 6.8.
+The VM allows restricted host-based ssh access from two secure OTP only administrative systems.
+The Jenkins GUI presented additional challenges.
+The Jenkins GUI is configured to log in as a standard user account with pass-wordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM.
 We restricting access to the physical VM and Jenkins GUI (bwjenkins) utilizing iptables, SSL and OTP.
-The VM allows restricted host-based ssh (port 22) access from two secure OTP only administrative systems.
-The Jenkins GUI presented additional challenges.
-We setup reverse proxy to run Jenkins behind apache/http with SSL for access to the administrative console.
+A reverse proxy was used to run Jenkins behind apache/http with SSL for access to the administrative console.
 All the configuration is in /etc/httpd/config.d/ssl.conf.
-An anonymous GUI view was setup (config file snippets below)
+Anonymous access to the Jenkins GUI was allowed for limited read only view of test status and historical plots.
+The Anonymous access view is not restricted.
+\\
+(config file snippets below)
 
@@
 \end{lstlisting}
-
-\subsection{Configuration Choices}
 

### 2017-03-03 manuscript/manuscript.tex

@@
 
+\subsection{LDAP with Jenkins}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
+\caption{ Use LDAP with Jenkins }
+\label{fig:LDAP-Jenkins}
+\end{figure}
+
+From the console view, select Manage Jenkins, select Configure Global Security.
+In the Security Realm section select the Advanced...
+tab.
+Input your LDAP server name and root DN.
+Click the Test Button.\\
+\\
+My first stab at this failed as an anonymous connection to our LDAP because we are using a local CA.
+WARNING: Failed to search LDAP for username, 
+sun.security.provider.certpath.SunCertPathBuilderException:
+unable to find valid certification path to requested target\\
+\\
+Had to add our certificate to the keystore:
+/usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
+Enter keystore password: Trust this certificate? [no]:  yes\\
+Certificate was added to keystore
+
+\subsection{Configure Global Security}
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{Configure-Global-Security}
+\caption{ Configure Global Security }
+\label{fig:Configure-Global-Security}
+\end{figure}
+We are allowing access by username and LDAP groups.
+The permissions can be scoped for individuals and groups.
+An example is removing Job delete permissions to prevent one user or group from deleting others jobs.
+
 \section{Anatomy of A Test}

### 2017-03-03 manuscript/manuscript.tex

@@
 \subsection{IOR Lustre scratch test}
-We created Jenkins tests to run the IOR MPI parallel filesystem test to run at a modest scale and validate filesystem functionality and performance for the scratch filesystem on a periodic basis.
-The test is scaled to provide representative performance numbers for a typical small application while not creating issues with other jobs or the filesystem at large.
-One of our best practices is to provide a management level summary description for casual jenkins users who want to view the test but do not need to understand the jenkins configuration and execution details.
+We created Jenkins tests to periodically run the IOR MPI parallel i/o benchmark at modest scale and validate filesystem functionality and performance for the scratch filesystem.
+The test is scaled to provide representative performance numbers for a typical small application while not creating performance issues with other jobs or the larger filesystem.
+One of our best practices is to provide a management level summary description for casual jenkins users who want to view the tests but do not need to understand the full Jenkins configuration and execution details.
 \begin{figure}[H]
@@
 \end{figure}
-Where possible, tests build from source and exercise multiple user-facing system components such as: git for external connectivity and loading modules to test the defaults in the environment.
-Where scripts on the SSH site are used, they are echoed and/or displayed with "cat -n" to make console output verbose and easy to debug in case of errors.
-
+Where possible, tests build from source and exercise multiple user-facing system components such as: git for external connectivity and modules to test defaults in the environment.
+Where scripts on the remote SSH site are used, they are echoed and/or displayed with "cat -n" to make console output verbose and easy to debug in case of errors.
 \begin{figure}[H]
@@
 \end{figure}
-
-The test is set to run as scheduled by Jenkins with a best-effort through our batch system.
-The test blocks such that the next test will not start until the previous one has completed.
-We employ a watchdog script to block the exit from the test until the batch system marks it as finished.
-
-\begin{lstlisting}[float,frame=tb,captionpos=t,language=bash,caption={pbs/torque watchdog script}, label=lst:watchdog]
+The IOR test is set to run as scheduled by Jenkins with a best-effort through our batch system.
+The test synchronously blocks such that the next test will not start until the previous one has completed.
+We employ a watchdog script to monitor the batch queue and keep the test active until the system marks it as finished.
+This has the side effect of making the minimum test time an integer multiple of the sleep time in the watchdog script.
+This may be adjusted to fit individual site needs.
+\begin{lstlisting}[frame=tb,captionpos=t,language=bash,caption={pbs/torque watchdog script}, label=lst:watchdog]
 #!/bin/bash
@@
 \end{figure}
-For tests that produce an interesting performance metric like IOR, we save that output to a file and use the Jenkins plotting feature to produce plots. 
+For tests that produce an interesting performance metric like IOR, we save that output to the file format expected by Jenkins and use plotting feature to produce plots. 
+\begin{lstlisting}[frame=tb,captionpos=t,language=bash,caption={sample YVALUE output file}, label=lst:yvalue]
+bwjenkins$ cat myiorREADnumber.dat 
+YVALUE=8352.71
+\end{lstlisting}
 \begin{figure}[H]
@@
 \end{figure}
-A plot like this helps us with performance baselines and we can quickly react to changes in the software environment or filesystem configuration.
+A plot like this helps us with performance baselines and we can quickly react to changes in the software environment or filesystem configuration that adversely impact performance.
 
@@
 An additional best practice is to enable E-mail Notifications to the test author and/or other interested parties.
-E-mail for unstable builds will cause an E-mail every time the test state changes (from successful to failing and again when back to successful ).
+Setting notifications for unstable builds will trigger an E-mail every time the test state changes (from successful to failing and again when back to successful ).
 \begin{figure}[H]
@@
 Our Jenkins instance is a source of information for a filesystem dashboard display we maintain in our wiki.
-The http:// urls for the plot images are shown on the dashboard and provide a recent-time display of filesystem metrics from a user point of view.
-We add a Jenkins test to track the response time of /bin/ls on the login nodes--a reasonable metric of metadata server health and also the number one issue reported by users when we are having filesystem issues.
+The "http://" urls for the plot images are shown on the dashboard and provide a recent-time display of filesystem metrics from a user point of view.
+We add a Jenkins test to track response time of /bin/ls on the login nodes--a reasonable metric of metadata server health and also the most common problem reported by users when we are having filesystem issues.
 \begin{figure}[H]
@@
 \subsection{special projects}
-The tabs display of our Jenkins instance is used to group tests and we add tabs for special projects.
+The initial display tabs in our Jenkins instance are used to group tests and we add tabs for special projects.
 For example we clone existing tests for evaluating a new software stack on our test login node.
-Our test rack has a separate set of tests from our production system and is used as our Jenkins test development area.
-The sustained petascale performance benchmarks are in their own tab since they can run at scale and are only run on-demand (not scheduled by Jenkins ).
+Our test rack has a separate set of tests from our production system and is used as our Jenkins development mule.
+The sustained petascale performance benchmarks are in their own tab because they run at scale and are only run on-demand by staff (not scheduled by Jenkins ).
 \begin{figure}[H]

### 2017-03-03 manuscript/manuscript.tex

@@
 %
-\author{\IEEEauthorblockN{Author1, Timothy Bouvet, Galen Arnold}
+\author{\IEEEauthorblockN{Timothy Bouvet, Reuben Budiardja, Galen Arnold}
 %xxxx\IEEEauthorrefmark{3} and
@@
 %\IEEEauthorblockA{\IEEEauthorrefmark{1}National Institute for Computational Science\\
+National Center for Supercomputing Applications\\
+University of Illinois at Urbana-Champaign, 61801\\
 National Institute for Computational Sciences\\
 The University of Tennessee, Knoxville, TN 37996\\
-\{email1,tbouvet@illinois.edu,gwarnold@illinois.edu\}@domain.edu}
+\{tbouvet@illinois.edu,reubendb@utk.edu,gwarnold@illinois.edu\}}
 %\IEEEauthorblockA{\IEEEauthorrefmark{4}Electrical Engineering and Computer Science Department\\University of Tennessee, Knoxville, TN 37996\\xx@eecs.utk.edu}
@@
 We evaluated test frameworks such as Inca [1] and Jenkins [2].
-Jenkins was chosen for its versatility, large user base, and multitudes of plugins including plotting test results over time.
+Jenkins was chosen for its versatility, large user base, and multitude of plugins including plotting test results over time.
 We utilize these plots to track trends and alert us to system-level issues before they are reported by our partners (users).
@@
 Security was of the highest concern since Jenkins has the ability to execute commands on our login nodes.
-Jenkins is set to log in as a standard user account with pass-wordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM.
+Jenkins is set to log in as a standard user account with password-less access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM.
 The VM (bwjenkins) was closely vetted by our security team on our test and development system (TDS) before it was allowed access to Blue Waters.
@@
 During a test, Jenkins downloads software, builds the software, submits a job, awaits completion, gathers and plots the results or returns error information during a failure.
-These are full end to end functionality testing of the programming environment, queueing system, license servers and provide historical metrics to quickly detect regressions.
+These are full end to end functionality tests of the programming environment, queueing system, license servers and they provide historical metrics to quickly detect regressions.
 
@@
 We will also show some application-based system-level tests we have implemented in Jenkins and share results of those tests.
-The deployment of Jenkins allow us to monitor and detect issues as early as possible from the perspective of a user on Blue Waters, eventually providing a more efficient service for better user experience.
+The deployment of Jenkins allows us to monitor and detect issues as early as possible from the perspective of a user on Blue Waters, eventually providing a more efficient service for better user experience.
 \end{abstract}
@@
 \section{Motivation}
-
-\begin{lstlisting}[float,frame=tb,captionpos=t,language=bash,caption={Apache Configuration Example}, label=lst:apacheconfig]
-
-# First, we configure the "default" to be a very 
-# restrictive set of features.  
-#
-<Directory />
-    Options FollowSymLinks
-    AllowOverride None  
-</Directory>
-
-\end{lstlisting}
 

### 2017-03-05 manuscript/manuscript.tex
swtools and more

@@
 \section{Motivation}
-
+Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance.
+Another requirement was to find an automated solution for running a suite of test jobs that reveal the system health after upgrades and outages before returning the system to service.
 \section{Jenkins Configuration}
@@
 \subsection{Introduction to Jenkins}
+Jenkins [2] is a self-contained, open source automation server which can be used to automate all sorts of tasks such as building, testing, and deploying software.
+Jenkins can be installed through native system packages, Docker, or even run standalone by any machine with the Java Runtime Environment installed.
+To install from rpm as root:
+wget -O /etc/yum.repos.d/jenkins.repo http://pkg.jenkins-ci.org/redhat/jenkins.repo
+rpm --import https://jenkins-ci.org/redhat/jenkins-ci.org.key
+yum install jenkins
 \subsection{Master-Node Configuration}
+We added a standard user account to our cluster that will execute the Jenkins tests.
+Unique ssh keys were generated on the Jenkins Server for accessing the user account on production and test environments.
+The keys on the server are located in Jenkins home directory (/var/lib/jenkins/.ssh).
+Using the GUI management console, the keyfile location and passphrase was entered under Manage Jenkins, Configure System, SSH remote hosts section.
+A unique SSH site is configured for our TDS, production and development login nodes.
+
 \subsection{Accessing Login Nodes}
+The ssh public key generated on Jenkins Server was deployed in the login node user account. The login node sshd_config was modified to allow Public Key Authentication from the Jenkins Server IP.
 
@@
 A reverse proxy was used to run Jenkins behind apache/http with SSL for access to the administrative console.
-All the configuration is in /etc/httpd/config.d/ssl.conf.
+All the configuration is in /etc/httpd/conf.d/ssl.conf.
 Anonymous access to the Jenkins GUI was allowed for limited read only view of test status and historical plots.
@@
 
-/etc/httpd/config.d/ssl.conf:
+/etc/httpd/conf.d/ssl.conf:
 Listen 443
@@
 \subsection{LDAP with Jenkins}
-
 \begin{figure}[H]
@@
 \end{figure}
-
-From the console view, select Manage Jenkins, select Configure Global Security.
+To enable LDAP, the LDAP Plugin was installed.
+To configure, from the console view, select Manage Jenkins, select Configure Global Security.
 In the Security Realm section select the Advanced...
@@
 \label{sec:SWToolsIntegration}
+\subsection{SWTools with Jenkins}
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{swtools-Jenkins}
+\caption{ Use SWTools with Jenkins }
+\label{fig:swtools-jenkins}
+\end{figure}
+
+\subsection{SWTools with Lammps}
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{swtools-lammps-jenkins}
+\caption{ SWTools with Lammps }
+\label{fig:swtools-lammps-jenkins}
+\end{figure}
 
@@
 % references section
+\section*{References}
+[1] http://inca.sdsc.edu/ Inca Monitoring: periodic, automated, user-level cyberinfrastructure testing
+[2] https://jenkins.io/ Jenkins: open source automation server written in Java
 

### 2017-03-07 manuscript/manuscript.tex
Add files via upload
fixed grammar issues

--- 2017-03-03 manuscript/manuscript.tex
@@
 
-From the console view, select Manage Jenkins, select Configure Global Security.
+To enable LDAP, the LDAP Plugin was installed.
+To configure, from the console view, select Manage Jenkins, select Configure Global Security.
 In the Security Realm section select the Advanced...
@@
 \\
-Had to add our certificate to the keystore:
+We had to add our certificate to the keystore:
 /usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
@@
 The permissions can be scoped for individuals and groups.
-An example is removing Job delete permissions to prevent one user or group from deleting others jobs.
+An example is removing Job delete permissions to prevent one user or group from deleting each other's jobs.
 
@@
 \end{figure}
-For tests that produce an interesting performance metric like IOR, we save that output to the file format expected by Jenkins and use plotting feature to produce plots. 
+For tests that produce an interesting performance metric like IOR, we save that output to the file format expected by Jenkins and use the plotting feature to produce plots. 
 \begin{lstlisting}[frame=tb,captionpos=t,language=bash,caption={sample YVALUE output file}, label=lst:yvalue]
@@
 An additional best practice is to enable E-mail Notifications to the test author and/or other interested parties.
-Setting notifications for unstable builds will trigger an E-mail every time the test state changes (from successful to failing and again when back to successful ).
+Setting notifications for unstable builds will trigger an E-mail every time the test state changes (from successful to failing and once again when successful ).
 \begin{figure}[H]

### 2017-03-07 manuscript/manuscript.tex
Cleaned up text

--- 2017-03-05 manuscript/manuscript.tex
@@
 The Jenkins GUI is configured to log in as a standard user account with pass-wordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM.
-We restricting access to the physical VM and Jenkins GUI (bwjenkins) utilizing iptables, SSL and OTP.
+We restricting access to the physical VM (bwjenkins) and the Jenkins GUI utilizing iptables, SSL and OTP.
 A reverse proxy was used to run Jenkins behind apache/http with SSL for access to the administrative console.
@@
 \label{sec:TestAnatomy}
+New software projects are required to be tested on our TDS and approved before deployment on Blue Waters.
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{swtools-lammps-jenkins}
+\includegraphics[width=0.5\textwidth]{swtools-lammps}
 \caption{ SWTools with Lammps }
-\label{fig:swtools-lammps-jenkins}
+\label{fig:swtools-lammps}
 \end{figure}

### 2017-03-08 manuscript/manuscript.tex
anatomy of a test
added subsections

@@
 \label{sec:TestAnatomy}
-New software projects are required to be tested on our TDS and approved before deployment on Blue Waters.
+New software projects are required to be tested on our TDS and approved before deployment on Blue Waters and this is one of our key best practices.
+Once a test is deployed it is assigned to a specific Jenkins tab via the "Edit View" link associated with that tab.
+Tests still in development reside in the "All" tab view until they have been peer reviewed by at least one other test developer.
+\subsection{test description}
+We require a description for each test to describe: what is tested, resources used by the test, intent of the test, and scheduling frequency.
+\subsection{limits log files}
+The Jenkins test VM filled to capacity after the first few weeks of intensive use and an influx of several new tests that output long source code build detail.
+We retroactively modified all tests to limit the number of old build logs retained (max 50 for most tests).
+\subsection{ssh to a login host}
+There are several target ssh hosts which may be selected from our instance: the test rack JYC, the main system, and the new software deployment login node within the main system.
+None of our tests run locally within the Jenkins VM.
+\subsection{run shell commands}
+A test is composed of shell command and where possible we try to be as transparent with our test construction as possible.
+We prefer commands in the Jenkins configuration over running a script in the filesystem on the remote ssh target.
+Scripts that are remote run with verbose mode or are displayed via "cat -n" to save output to the Jenkins console log and make for simpler debugging when a test fails.
+\subsubsection{test completes on login node}
+Some tests run only on the ssh login node and return more or less immediately.
+Examples include tests for batch system functionality, ssh functionality, and filesystem functionality.
+These tests are very similar in style to unit tests which target a limited set of functionality.
+\subsubsection{test is submitted to batch system}
+More comprehensive tests typically build and run an application or benchmark through the batch system.
+These tests exercise multiple aspects of the system: (filesystem, compilers and modules, high-speed network, external connectivity to the internet...).
+They block to completion so that we do not overburden the batch system with tests.
+Unlike tests that run entirely on a login node, completion time can be highly variable depending on the queue depth and available backfill windows for the batch system.
+\subsection{post test actions}
+\subsubsection{scp files back to Jenkins host}
+Most comprehensive tests produce output that we use when debugging a failed test.
+They may also produce plot data.
+These files are copied back to the Jenkins host so that they can be viewed and/or incorporated into the plot feature of Jenkins.
+\subsubsection{plots}
+Successful tests save plot files and contribute a new data point to a plot.
+The Jenkins server accumulates the data as rows in a spreadsheet (under /var/lib/jenkins/jobs/ ) and plots them via the "Plots" link for a test.
+\subsection{email notification}
+When the state of a test changes, email notification is sent to the test owner.
+As a best practice we also use the email notification as a method of tracking authorship and each test has an email owner even if notifications are disabled for the test.
 
@@
 \section{Conclusion}
+\subsection{caveats}
+Transient errors with Jenkins sometimes occur--particularly with the Jenkins ssh subsystem.
+It's not unusual to get failure rates of 1/100 from an ssh failure which is completely transient (immediately running the test again manually clears the issue on the dashboard).
 \label{sec:conclusion}

### 2017-03-08 manuscript/manuscript.tex
added Best Practices section
Best Practices section draft

@@
 
+\section{Best Practices}
+\begin{itemize}
+\item Tests are developed on the JYC development rack and not assigned into a Jenkins tab until reviewed.
+\item Email notification is enabled for most tests and the field is always populated with a test owner.
+\item All tests contain a description that describes what is tested, resources required, scheduling frequency, and overall summary  to be readable by the management team.
+\item Log file count is limited in the test configuration to keep from filling filesystem space with verbose logs.
+\item Tests are coded to be more verbose than necessary so that failures can be isolated quickly and easily.
+\end{itemize}
+
 \section{Conclusion}

### 2017-03-13 manuscript/manuscript.tex
Added short abstract

@@
 Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance.
+Jenkins was chosen for its versatility, large user base, and multitudes of plugins including plotting test results over time.
+We utilize these plots to track trends and alert us to system-level issues before they are reported by our partners (users).
+Not only does Jenkins have the ability to store historical data, but it can also send email or text pages based on results of a test.
+Other requirements we had include two-factor authentication for accessing Jenkins GUI with administrator privileges and account management through LDAP.
+In this paper we describe our experience in deploying Jenkins as user-level system-wide regression testing and monitoring framework for Blue Waters.
+\end{abstract}
+
+\begin{IEEEkeywords}
+Performance; Benchmarking; Computer architecture
+\end{IEEEkeywords}
+
+\begin{abstract}
+LONG-This paper will explore the challenges of regression testing and monitoring of large scale systems such as NCSA’s Blue Waters.
+Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance.
 Another requirement was to find an automated solution for running a suite of test jobs that reveal the system health after upgrades and outages before returning the system to service.
@@
 
-\begin{IEEEkeywords}
-Performance; Benchmarking; Computer architecture
-\end{IEEEkeywords}
-
 % For peer review papers, you can put extra information on the cover
@@
 Jenkins can be installed through native system packages, Docker, or even run standalone by any machine with the Java Runtime Environment installed.
-To install from rpm as root:
-wget -O /etc/yum.repos.d/jenkins.repo http://pkg.jenkins-ci.org/redhat/jenkins.repo
-rpm --import https://jenkins-ci.org/redhat/jenkins-ci.org.key
+To install from rpm as root for centos:
+wget -O /etc/yum.repos.d/jenkins.repo http://pkg.jenkins-ci.org/redhat-stable/jenkins.repo
+rpm --import https://jenkins-ci.org/redhat-stable/jenkins-ci.org.key
 yum install jenkins
@@
 The Anonymous access view is not restricted.
-\\
-(config file snippets below)
 
 \begin{lstlisting}
+(Jenkins sever configuration file snippets below)
 /etc/ssh/sshd_config:
@@
 /etc/httpd/conf.d/ssl.conf:
-Listen 443
-<VirtualHost _default_:443>
-SSLSessionCache         shmcb:/var/cache/mod_ssl/scache
-SSLSessionCacheTimeout  300
-ServerName bwjenkins.ncsa.illinois.edu:443
  # -- The following sets ReverseProxy for Jenkins
@@
 
+ # -- The following sets OTP for Jenkins SSL connection
   DefineExternalAuth pwauth+session pipe /usr/local/bin/
@@
   </LocationMatch>
+
+ /usr/local/bin/pwauth+session: https://github.com/reubendb/
+ BasicAuthOTPSession/blob/master/BasicAuthOTPSession.py#L1
 \end{lstlisting}
-
 \subsection{LDAP with Jenkins}
@@
 \section{Conclusion}
+\subsection{reproducibility and regression testing}
+\subsection{rapid reaction}
 \subsection{caveats}
@@
 \section*{Acknowledgment}
-This research used resources at the National Institute for Computational Sciences, funded by the National Science Foundation (NSF).
+This research used resources at the National Institute for Computational Sciences and the National Center for Supercomputing Applications, funded by the National Science Foundation (NSF).
 

### 2017-03-13 manuscript/manuscript.tex
Draft on introduction.

@@
 
-\section{Motivation}
-Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance.
-Another requirement was to find an automated solution for running a suite of test jobs that reveal the system health after upgrades and outages before returning the system to service.
+\section{Introduction}
+
+Monitoring large and complex high-performance computing systems has many challenges.
+Layers and multiple versions of software stack, system-level configurations, (parallel) file systems, diversity in users need and usage, and variable network traffics all interact to increase the system's complexity.
+Although there exist monitoring systems for each of these components, they often do not capture the behavior of the system in aggregate, which in fact is what users and their applications experience.
+Therefore an application-level system monitoring is needed to give us a more complete picture of the system behavior.
+
+Over time, either due to configuration changes or hardware aging, performance of such complex system may regress.
+To identify and correct such regression, one must have some method to do regression testing of the system performance.
+This requires systematic record of the the system performance over time.
+
+These two requirements can be concisely summarized as an ``application-level regression testing''.
+Our goal was then to come up with an automated solution for running these user-level regression tests to evaluate system usability and performance.
+For this purpose we have chosen to use Jenkins\footnote{http://jenkins.io}.
+
+%Another requirement was to find an automated solution for running a suite of test jobs that reveal the system health after upgrades and outages before returning the system to service.
 \section{Jenkins Configuration}
@@
 \subsection{SWTools with Jenkins}
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.5\textwidth]{swtools-Jenkins}
-\caption{ Use SWTools with Jenkins }
-\label{fig:swtools-jenkins}
-\end{figure}
+%\begin{figure}[H]
+%\centering
+%\includegraphics[width=0.5\textwidth]{swtools-Jenkins}
+%\caption{ Use SWTools with Jenkins }
+%\label{fig:swtools-jenkins}
+%\end{figure}
 

### 2017-03-13 manuscript/manuscript.tex
text edits and conclusion
worked on conclusion and fixed a few grammar issues here and there for
readability

--- 2017-03-13 manuscript/manuscript.tex
@@
 Not only does Jenkins have the ability to store historical data, but it can also send email or text pages based on results of a test.
-Other requirements we had include two-factor authentication for accessing Jenkins GUI with administrator privileges and account management through LDAP.
-In this paper we describe our experience in deploying Jenkins as user-level system-wide regression testing and monitoring framework for Blue Waters.
+Other requirements we had include two-factor authentication for accessing the Jenkins GUI with administrator privileges and account management through LDAP.
+In this paper we describe our experience in deploying Jenkins as a user-level system-wide regression testing and monitoring framework for Blue Waters.
 \end{abstract}
@@
 To install from rpm as root for centos:
-wget -O /etc/yum.repos.d/jenkins.repo http://pkg.jenkins-ci.org/redhat-stable/jenkins.repo
-rpm --import https://jenkins-ci.org/redhat-stable/jenkins-ci.org.key
+\begin{lstlisting}
+wget -O /etc/yum.repos.d/jenkins.repo \
+  http://pkg.jenkins-ci.org/redhat-stable/jenkins.repo
+rpm --import \
+  https://jenkins-ci.org/redhat-stable/jenkins-ci.org.key
 yum install jenkins
+\end{lstlisting}
 \subsection{Master-Node Configuration}
@@
 The access control is set to "Jenkins' own user database," and the "Allow users to sign up" option is enabled, so if you don't have an account, you can create one by providing your name, e-mail and a password.
-Additionally, there's an authorization option enabled which says "Logged-in users can do anything." So, once you complete the sign up form, you have full admin access to the system.
+Additionally, there's an authorization option enabled which says "Logged-in users can do anything." So, once signed in, you have full admin access to the Jenkins system instance.
 This required us initially to test the deployment with our test and development (TDS) CRAY.
-This resulted in the following requirements.
-Restricted OTP access to the physical system that will host Jenkins.
-In addition, OTP only access to the Jenkins GUI command console that must be contained within our IP space.
+This resulted in the following requirement: restricted OTP access to the physical system hosting Jenkins.
+In addition, OTP only access to the Jenkins GUI command console must be contained within our IP space.
 The Jenkins GUI will also restrict the command console access to our Blue Waters LDAP server.
@@
 \subsection{Configuration Choices}
-Jenkins instance was deployed on a vSphere managed VM running Centos 6.8.
+The Jenkins instance was deployed on a vSphere managed VM running Centos 6.8.
 The VM allows restricted host-based ssh access from two secure OTP only administrative systems.
 The Jenkins GUI presented additional challenges.
-The Jenkins GUI is configured to log in as a standard user account with pass-wordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM.
-We restricting access to the physical VM (bwjenkins) and the Jenkins GUI utilizing iptables, SSL and OTP.
+The Jenkins GUI is configured to log in as a standard user account with password-less access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM.
+We restrict access to the physical VM (bwjenkins) and the Jenkins GUI utilizing iptables, SSL and OTP.
 A reverse proxy was used to run Jenkins behind apache/http with SSL for access to the administrative console.
@@
 To enable LDAP, the LDAP Plugin was installed.
-To configure, from the console view, select Manage Jenkins, select Configure Global Security.
+To configure, from the console view, select Manage Jenkins, then select Configure Global Security.
 In the Security Realm section select the Advanced...
@@
 \subsection{reproducibility and regression testing}
+Jenkins provides the framework we need to maintain tests in a consistent fashion and track the results over time (logs and plots ).
+Tests typically are not changed so that we get apples-apples comparisons.
+When a new test is needed for a particular activity, we attempt to derive it from an existing test to maintain consistency and simplify test creation.
+Reusable test components (watchdog scripts, plotting metrics) are employed to make construction of completely new tests straightforward.
 \subsection{rapid reaction}
+The notification feature keeps test owners engaged in the testing activity of Jenkins and they are often our first responders to system issues.
+This results in a shorter reaction time when the system is not performing to expectations--staff are notified automatically when the user experience is impacted.
 \subsection{caveats}
+\subsubsection{transient errors}
 Transient errors with Jenkins sometimes occur--particularly with the Jenkins ssh subsystem.
-It's not unusual to get failure rates of 1/100 from an ssh failure which is completely transient (immediately running the test again manually clears the issue on the dashboard).
+It's not unusual to get ssh failure rates of 1/100 which are completely transient (immediately running the test again manually clears the issue on the dashboard).
+\subsubsection{test scale and frequency}
+There is some subjectivity in the frequency and scale (resource utilization) of tests.
+Testing too often, too large, or some combination of the two may perturb the system such that other tests are impacted or create bottlenecks in the system for the real user community.
+This is the primary reason we require peer review for new tests.
 \label{sec:conclusion}

### 2017-03-16 manuscript/manuscript.tex
Further work on introduction.

@@
 
-\section{Motivation}
-Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance.
+\section{Introduction}
+\label{sec:introduction}
+
+Monitoring large and complex high-performance computing systems has many challenges.
+Layers and multiple versions of software stack, system-level configurations, (parallel) file systems, diversity in users need and usage, and variable network traffics all interact to increase the system's complexity.
+Although there exist monitoring systems for each of these components, they often do not capture the behavior of the system in aggregate, which in fact is what users and their applications experience.
+Therefore an application-level system monitoring is needed to give us a more complete picture of the system behavior.
+
+Over time, either due to configuration changes or hardware aging, performance of such complex system may regress.
+To identify and correct such regression, one must have some method to do regression testing of the system performance.
+This requires systematic record of the the system performance over time.
+
+These two requirements can be concisely summarized as an ``application-level regression testing''.
+Our goal was then to come up with an automated solution for running these user-level regression tests to evaluate system usability and performance.
+For this purpose we have chosen to use Jenkins\footnote{http://jenkins.io}.
+
+Jenkins is an open source automation server.
+Although it is typically used as continuous integration tool in software development process, its wide-ranging features makes it suitable for any task that can be automated.
+These tasks may include building applications, executing them, deploying software, and running various custom-written tests and scripts.
+We chose Jenkins as the tool for our regression testing framework because its active development, wide community support, and the readily available ``plugins'' to perform various specific tasks.
+
+In this paper we describe in details our experience in using Jenkins to perform application-level regression testing on high-performance computing systems such as the Blue Water supercomputer at the National Center for Supercomputing Application, Darter and Beacon at the National Institute for Computational Sciences (NICS).
+These systems are Cray XK, XC, and CS series.
+The outline of this paper is as follows.
+[NEED TO WRITE THIS]
+
+%Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance.
 Another requirement was to find an automated solution for running a suite of test jobs that reveal the system health after upgrades and outages before returning the system to service.
+
 \section{Jenkins Configuration}
@@
 
-\subsection{Introduction to Jenkins}
-Jenkins [2] is a self-contained, open source automation server which can be used to automate all sorts of tasks such as building, testing, and deploying software.
+% \subsection{Introduction to Jenkins}
+% Jenkins [2] is a self-contained, open source automation server which can be used to automate all sorts of tasks such as building, testing, and deploying software.
 Jenkins can be installed through native system packages, Docker, or even run standalone by any machine with the Java Runtime Environment installed.
-To install from rpm as root for centos:
-\begin{lstlisting}
-wget -O /etc/yum.repos.d/jenkins.repo \
-  http://pkg.jenkins-ci.org/redhat-stable/jenkins.repo
-rpm --import \
-  https://jenkins-ci.org/redhat-stable/jenkins-ci.org.key
-yum install jenkins
-\end{lstlisting}
+% To install from rpm as root for centos:
+% \begin{lstlisting}
+% wget -O /etc/yum.repos.d/jenkins.repo \
+%   http://pkg.jenkins-ci.org/redhat-stable/jenkins.repo
+% rpm --import \
+%   https://jenkins-ci.org/redhat-stable/jenkins-ci.org.key
+% yum install jenkins
+% \end{lstlisting}
+
 \subsection{Master-Node Configuration}

### 2017-03-17 manuscript/manuscript.tex

@@
 % \end{lstlisting}
+
+Jenkins is typically available from the package repository of most major linux distribution of choice.
+One can also download and install Jenkins directly from its website.
+We used the RPM package to install Jenkins on a CentOS virtual machine (VM).
+Jenkins comes with its own web server so that managing and accessing Jenkins can be done via any web browser (in the next section we discuss using Apache HTTP Server in front of Jenkin's for better security).
+Typically Jenkins's web server listen to port 8080, but this is configurable.
+
+Jenkins has an implicit assumption that the machine on which it is installed is also the primary machine being used to build and test the software.
+In our case, this is not what we would want.
+In fact, our applications will be built on the HPC system on which we intent to run the tests (typically on the login nodes), and will be run on the compute nodes of the HPC system (i.e.
+via batch job submission to the job queueing system).
+This is because not only we want to test the runtime performance of the applications, but also we want to ensure that the software and programming environment of the system can still build the applications correctly.
+Incidentally, the latter also informs us any user-level problem such as slow or overloaded login nodes, slow file system access, erroneous or incompatible default software (library, compilers, etc) versions.
+In short, we want our tests to simulate typical workflow of a user on the system being testing.
+
+Therefore what we need is a mechanism to execute a ``project'' --- a user-configured description of work which Jenkins should perform such as building a piece of software, in Jenkins jargon --- on remote machines (``remote'' from the perspective of Jenkins).
+In this case, the Jenkins machine simply manages the automation scheduling, shows status of projects in execution (``builds'' in Jenkins jargon) , and archives results of the tests (i.e.
+``artifact'').
+It also provides the user interface (via its own web server) to create and configure projects.
+These tasks are sufficiently light weight such that Jenkins can be installed on a VM with sufficient disk space for the artifacts, since the trully heavy lifting on building and executing the application tests are done on the remote machine.
+
+There are two ways to achieve executing builds on remote machine.
+Each has their own benefits, and whichever way to use is a matter of choice.
+One may use Jenkin's core feature of adding ``Nodes`` to its environment.
+One may also use a Jenkins plugin called ''SSH Plugin`` to allow execution on remote machine via SSH protocol.
+At NICS our setup uses the former, while at NCSA our setup uses the latter.
+In the following we briefly discuss the setup of these two mechanisms.
 

### 2017-03-18 manuscript/manuscript.tex
Cleaned up some typos
Nice intro Rueben

@@
 
-\begin{abstract}
-LONG-This paper will explore the challenges of regression testing and monitoring of large scale systems such as NCSA’s Blue Waters.
+%\begin{abstract}
+%LONG-This paper will explore the challenges of regression testing and monitoring of large scale systems such as NCSA’s Blue Waters.
 Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance.
@@
 
-Our Jenkins instance was deployed on a vSphere managed VM running Centos 6.8.
+%Our Jenkins instance was deployed on a vSphere managed VM running Centos 6.8.
 Security was of the highest concern since Jenkins has the ability to execute commands on our login nodes.
@@
 
-In this paper we describe in detail our challenges and experiences in deploying Jenkins as a user-level system-wide regression testing and monitoring framework for Blue Waters.
+%In this paper we describe in detail our challenges and experiences in deploying Jenkins as a user-level system-wide regression testing and monitoring framework for Blue Waters.
 We will also show some application-based system-level tests we have implemented in Jenkins and share results of those tests.
 The deployment of Jenkins allows us to monitor and detect issues as early as possible from the perspective of a user on Blue Waters, eventually providing a more efficient service for better user experience.
-\end{abstract}
+%\end{abstract}
 
@@
 
-Monitoring large and complex high-performance computing systems has many challenges.
-Layers and multiple versions of software stack, system-level configurations, (parallel) file systems, diversity in users need and usage, and variable network traffics all interact to increase the system's complexity.
+Monitoring large and complex high-performance computing systems have many challenges.
+Layers and multiple versions of the software stack, system-level configurations, (parallel) file systems, diversity in users need and usage, and variable network traffics all interact to increase the system's complexity.
 Although there exist monitoring systems for each of these components, they often do not capture the behavior of the system in aggregate, which in fact is what users and their applications experience.
-Therefore an application-level system monitoring is needed to give us a more complete picture of the system behavior.
+Therefore an application-level system monitoring framework is needed to give us a more complete picture of the system behavior.
 
-Over time, either due to configuration changes or hardware aging, performance of such complex system may regress.
+Over time, either due to configuration and software changes or hardware aging, performance of such complex system may regress.
 To identify and correct such regression, one must have some method to do regression testing of the system performance.
-This requires systematic record of the the system performance over time.
+This requires a systematic record of the system performance over time.
 
@@
 Jenkins is an open source automation server.
-Although it is typically used as continuous integration tool in software development process, its wide-ranging features makes it suitable for any task that can be automated.
+Although it is typically used as a continuous integration tool in the software development process, its wide-ranging features makes it suitable for any task that can be automated.
 These tasks may include building applications, executing them, deploying software, and running various custom-written tests and scripts.
-We chose Jenkins as the tool for our regression testing framework because its active development, wide community support, and the readily available ``plugins'' to perform various specific tasks.
+We chose Jenkins as the tool for our regression testing framework because of its active development, wide community support, and the readily available ``plugins'' to perform various specific tasks.
 
-In this paper we describe in details our experience in using Jenkins to perform application-level regression testing on high-performance computing systems such as the Blue Water supercomputer at the National Center for Supercomputing Application, Darter and Beacon at the National Institute for Computational Sciences (NICS).
-These systems are Cray XK, XC, and CS series.
+In this paper we describe in details our experience in using Jenkins to perform application-level regression testing on high-performance computing systems such as the Blue Water supercomputer at the National Center for Supercomputing Applications (NCSA), Darter and Beacon at the National Institute for Computational Sciences (NICS).
+These systems are Cray XE, XK, XC, and CS series.
 The outline of this paper is as follows.
@@
 via batch job submission to the job queueing system).
-This is because not only we want to test the runtime performance of the applications, but also we want to ensure that the software and programming environment of the system can still build the applications correctly.
-Incidentally, the latter also informs us any user-level problem such as slow or overloaded login nodes, slow file system access, erroneous or incompatible default software (library, compilers, etc) versions.
+This is because not only do we want to test the runtime performance of the applications, but also we want to ensure that the software and programming environment of the system can still build the applications correctly.
+Incidentally, the latter also informs us of any user-level problem such as slow or overloaded login nodes, slow file system access, erroneous or incompatible default software (library, compilers, etc) versions.
 In short, we want our tests to simulate typical workflow of a user on the system being testing.
@@
 It also provides the user interface (via its own web server) to create and configure projects.
-These tasks are sufficiently light weight such that Jenkins can be installed on a VM with sufficient disk space for the artifacts, since the trully heavy lifting on building and executing the application tests are done on the remote machine.
+These tasks are sufficiently light weight such that Jenkins can be installed on a VM with sufficient disk space for the artifacts, since the truly heavy lifting of building and executing the application tests are performed on the remote machine.
 
-There are two ways to achieve executing builds on remote machine.
-Each has their own benefits, and whichever way to use is a matter of choice.
+There are two ways to achieve an executing build on a remote machine.
+Each have their own benefits, and your selection is a matter of choice.
 One may use Jenkin's core feature of adding ``Nodes`` to its environment.
-One may also use a Jenkins plugin called ''SSH Plugin`` to allow execution on remote machine via SSH protocol.
+One may also use a Jenkins plugin called ''SSH Plugin`` to allow execution on a remote machine via SSH protocol.
 At NICS our setup uses the former, while at NCSA our setup uses the latter.
@@
 We restrict access to the physical VM (bwjenkins) and the Jenkins GUI utilizing iptables, SSL and OTP.
-A reverse proxy was used to run Jenkins behind apache/http with SSL for access to the administrative console.
+A reverse proxy was used to run Jenkins behind Apache HTTP Server with SSL for access to the administrative console.
 All the configuration is in /etc/httpd/conf.d/ssl.conf.
@@
 \section*{Acknowledgment}
-This research used resources at the National Institute for Computational Sciences and the National Center for Supercomputing Applications, funded by the National Science Foundation (NSF).
+This research used resources at the National Institute for Computational Sciences (NICS) and the National Center for Supercomputing Applications (NCSA), funded by the National Science Foundation (NSF).
 

### 2017-03-20 manuscript/manuscript.tex
wrapped an extended line a bit

@@
 
- # -- The following sets OTP for Jenkins SSL connection
-  DefineExternalAuth pwauth+session pipe /usr/local/bin/
-  pwauth+session
+ # -- OTP for Jenkins SSL connection
+   DefineExternalAuth pwauth+session pipe 
+   /usr/local/bin/pwauth+session
   <LocationMatch / > 
@@
 
- /usr/local/bin/pwauth+session: https://github.com/reubendb/
- BasicAuthOTPSession/blob/master/BasicAuthOTPSession.py#L1
+ /usr/local/bin/pwauth+session: 
+ https://github.com/reubendb/BasicAuthOTPSession
+ /blob/master/BasicAuthOTPSession.py#L1
 \end{lstlisting}

### 2017-03-22 manuscript/manuscript.tex
added to pwauth, https otp section

@@
 -A INPUT -s 172.16.0.0/15 -m state --state NEW -m tcp 
--p tcp --dport 22 -j ACCEPT *delete maybe*
+-p tcp --dport 22 -j ACCEPT 
 -A INPUT  -m state --state NEW -m tcp -p tcp --dport 80 
@@
 
+ NOTE: Install  mod_authnz_external native package
+
+  /etc/pam.d/pwauth:
+ #%PAM-1.0
+ auth	   required	/lib64/security/pam_securid.so
+ account    include      password-auth
+
  /usr/local/bin/pwauth+session: 
@@
  /blob/master/BasicAuthOTPSession.py#L1
+
 \end{lstlisting}

### 2017-03-23 manuscript/manuscript.tex
Worked on describing master-node using Jenkins built-in node.

--- 2017-03-18 manuscript/manuscript.tex
@@
 
-%\begin{abstract}
-%LONG-This paper will explore the challenges of regression testing and monitoring of large scale systems such as NCSA’s Blue Waters.
+\begin{abstract}
+LONG-This paper will explore the challenges of regression testing and monitoring of large scale systems such as NCSA’s Blue Waters.
 Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance.
@@
 
-%Our Jenkins instance was deployed on a vSphere managed VM running Centos 6.8.
+Our Jenkins instance was deployed on a vSphere managed VM running Centos 6.8.
 Security was of the highest concern since Jenkins has the ability to execute commands on our login nodes.
@@
 
-%In this paper we describe in detail our challenges and experiences in deploying Jenkins as a user-level system-wide regression testing and monitoring framework for Blue Waters.
+In this paper we describe in detail our challenges and experiences in deploying Jenkins as a user-level system-wide regression testing and monitoring framework for Blue Waters.
 We will also show some application-based system-level tests we have implemented in Jenkins and share results of those tests.
 The deployment of Jenkins allows us to monitor and detect issues as early as possible from the perspective of a user on Blue Waters, eventually providing a more efficient service for better user experience.
-%\end{abstract}
+\end{abstract}
 
@@
 
-Monitoring large and complex high-performance computing systems have many challenges.
-Layers and multiple versions of the software stack, system-level configurations, (parallel) file systems, diversity in users need and usage, and variable network traffics all interact to increase the system's complexity.
+Monitoring large and complex high-performance computing systems has many challenges.
+Layers and multiple versions of software stack, system-level configurations, (parallel) file systems, diversity in users need and usage, and variable network traffics all interact to increase the system's complexity.
 Although there exist monitoring systems for each of these components, they often do not capture the behavior of the system in aggregate, which in fact is what users and their applications experience.
-Therefore an application-level system monitoring framework is needed to give us a more complete picture of the system behavior.
+Therefore an application-level system monitoring is needed to give us a more complete picture of the system behavior.
 
-Over time, either due to configuration and software changes or hardware aging, performance of such complex system may regress.
+Over time, either due to configuration changes or hardware aging, performance of such complex system may regress.
 To identify and correct such regression, one must have some method to do regression testing of the system performance.
-This requires a systematic record of the system performance over time.
+This requires systematic record of the the system performance over time.
 
@@
 Jenkins is an open source automation server.
-Although it is typically used as a continuous integration tool in the software development process, its wide-ranging features makes it suitable for any task that can be automated.
+Although it is typically used as continuous integration tool in software development process, its wide-ranging features makes it suitable for any task that can be automated.
 These tasks may include building applications, executing them, deploying software, and running various custom-written tests and scripts.
-We chose Jenkins as the tool for our regression testing framework because of its active development, wide community support, and the readily available ``plugins'' to perform various specific tasks.
+We chose Jenkins as the tool for our regression testing framework because its active development, wide community support, and the readily available ``plugins'' to perform various specific tasks.
 
-In this paper we describe in details our experience in using Jenkins to perform application-level regression testing on high-performance computing systems such as the Blue Water supercomputer at the National Center for Supercomputing Applications (NCSA), Darter and Beacon at the National Institute for Computational Sciences (NICS).
-These systems are Cray XE, XK, XC, and CS series.
+In this paper we describe in details our experience in using Jenkins to perform application-level regression testing on high-performance computing systems such as the Blue Water supercomputer at the National Center for Supercomputing Application, Darter and Beacon at the National Institute for Computational Sciences (NICS).
+These systems are Cray XK, XC, and CS series.
 The outline of this paper is as follows.
-[NEED TO WRITE THIS]
+[FIXME: WRITE PAPER OUTLINE AFTER COMPLETE DRAFT]
 
@@
 via batch job submission to the job queueing system).
-This is because not only do we want to test the runtime performance of the applications, but also we want to ensure that the software and programming environment of the system can still build the applications correctly.
-Incidentally, the latter also informs us of any user-level problem such as slow or overloaded login nodes, slow file system access, erroneous or incompatible default software (library, compilers, etc) versions.
+This is because not only we want to test the runtime performance of the applications, but also we want to ensure that the software and programming environment of the system can still build the applications correctly.
+Incidentally, the latter also informs us any user-level problem such as slow or overloaded login nodes, slow file system access, erroneous or incompatible default software (library, compilers, etc) versions.
 In short, we want our tests to simulate typical workflow of a user on the system being testing.
 
-Therefore what we need is a mechanism to execute a ``project'' --- a user-configured description of work which Jenkins should perform such as building a piece of software, in Jenkins jargon --- on remote machines (``remote'' from the perspective of Jenkins).
-In this case, the Jenkins machine simply manages the automation scheduling, shows status of projects in execution (``builds'' in Jenkins jargon) , and archives results of the tests (i.e.
+Therefore what we need is a mechanism to execute a ``project'' --- a user-configured description of work which Jenkins should perform such as building a piece of software, in Jenkins parlance --- on remote machines (``remote'' from the perspective of Jenkins).
+In this case, the Jenkins machine simply manages the automation scheduling, shows status of projects in execution (``builds'' in Jenkins parlance) , and archives results of the tests (i.e.
 ``artifact'').
 It also provides the user interface (via its own web server) to create and configure projects.
-These tasks are sufficiently light weight such that Jenkins can be installed on a VM with sufficient disk space for the artifacts, since the truly heavy lifting of building and executing the application tests are performed on the remote machine.
+These tasks are sufficiently light weight such that Jenkins can be installed on a VM with sufficient disk space for the artifacts, since the trully heavy lifting on building and executing the application tests are done on the remote machine.
 
-There are two ways to achieve an executing build on a remote machine.
-Each have their own benefits, and your selection is a matter of choice.
+There are two ways to achieve executing builds on remote machine.
+Each has their own benefits, and whichever way to use is a matter of choice.
 One may use Jenkin's core feature of adding ``Nodes`` to its environment.
-One may also use a Jenkins plugin called ''SSH Plugin`` to allow execution on a remote machine via SSH protocol.
+One may also use a Jenkins plugin called ''SSH Plugin`` to allow execution on remote machine via SSH protocol.
 At NICS our setup uses the former, while at NCSA our setup uses the latter.
 In the following we briefly discuss the setup of these two mechanisms.
+
+\subsection{Using Nodes for Test Systems}
+The original idea behind adding nodes is to allow Jenkins to scale with the workload it has to do.
+As projects are added, one can add nodes (i.e.
+more build machines) allowing Jenkins to build more projects concurrently.
+Jenkin's project can also be explicitly 'labeled' to only be executed on a certain node.
+We capitalized both of these features to enable the aforementioned remote execution.
+
+For each HPC system login node, we created a Jenkins node\footnote{Do not be confused with multiple usage of the word ''node`` here.
+The former refers to the typical usage of login node in HPC.
+The latter refers to Jenkins' vernacular of ''node`` as previously defined}.
+We then labeled the (Jenkins) node with the name of the HPC system.
+For example, at NICS we have the labels 'beacon' and 'darter' to refer to the Cray CS-300 (Beacon) and XC-30 (Darter) login nodes, respectively.
+Each test application (i.e.
+''project``) is then labeled to ensure that they only run on the appropriate node.
+For example, we have used NAMD (FIXME: Need reference for NAMD) as an applicaton test.
+We would create a Jenkin project called ''NAMD-Beacon`` and label it to only run on ''beacon`` node.
+We would also create another project called ''NAMD-Darter`` and label it appropriately.
+The two projects have slighly different build scripts (and possibly different test cases) so that they build correctly on the systems they were meant to run on.
+
+Jenkins nodes need to have a Java-based daemon (Jenkins' ''slave.jar``) to run which connect back to the master via a certain port (which is configurable).
+This can be considered a drawback.
+If the daemon somehow dies, it needs to be restarted.
+The daemon runs as regular user, the user which essentially runs the build and submit the jobs on the HPC system.
+In our case, we created a user called ''jenkins`` with the same privilege as any other regular user.
+Both the extra port opening and the daemon itself may be considered as attack vectors from security perspective.
+At NICS however we consider this to be acceptable because of other mitigation (which we will discussed later).
+
+The benefit of this method is that one can basically treat the nodes as local environment in Jenkins, while having access to the HPC environment.
+For example, each node would have access to the parallel lustre filesystem mounted by the HPC system (even if Jenkins master itself does not, being only a small separate VM).
+Each node can define its lustre filesystem as its build and test workspace.
+Yet Jenkins automatically manages all communication with the nodes such that files (e.g.
+plot data, test output) generated on the lustre filesystem is readable from Jenkins without the explicit remote copy (i.e.
+via SCP).
+Another example is that one can have Jenkins checkout or clone code from remote repository (e.g.
+using Subversion or Git) and the copy will be automatically available on the lustre filesystem defined as the workspace of that node.
+These benefits integration makes building Jenkins project more seamless.
 
@@
 We restrict access to the physical VM (bwjenkins) and the Jenkins GUI utilizing iptables, SSL and OTP.
-A reverse proxy was used to run Jenkins behind Apache HTTP Server with SSL for access to the administrative console.
+A reverse proxy was used to run Jenkins behind apache/http with SSL for access to the administrative console.
 All the configuration is in /etc/httpd/conf.d/ssl.conf.
@@
 \section*{Acknowledgment}
-This research used resources at the National Institute for Computational Sciences (NICS) and the National Center for Supercomputing Applications (NCSA), funded by the National Science Foundation (NSF).
+This research used resources at the National Institute for Computational Sciences and the National Center for Supercomputing Applications, funded by the National Science Foundation (NSF).
 

### 2017-03-23 manuscript/manuscript.tex
Worked on SSH method. Tim's previous write up has been incorporated here (and is now commented out).

@@
 
-\subsection{Master-Node Configuration}
-We added a standard user account to our cluster that will execute the Jenkins tests.
+\subsection{Using SSH Plugins for Test Systems}
+The SSH plugin (FIXME: Need references) is another method for which one can access the HPC systems from Jenkins.
+As the name implies, Jenkins project with this type of build scripts simply SSH to the desired machine then execute the scripts there.
+
+The benefit of this method is that it more closely mimmicks (FIXME; spelling) how real users access the HPC system.
+There is no need for additional daemon to run on the HPC login nodes and there is no need for the corresponding opening of port on Jenkins VM.
+Because NCSA and NICS systems utilize two-factor RSA one-time password for users login, we needed to make slight modification so that Jenkins can have automated login.
+The login nodes \textttt{/etc/ssh/sshd_config} was modified to allow ''Public Key Authentication`` from the Jenkins VM unique IP address.
+Pairs of SSH keys with passphrase were generated on Jenkins VM with their public keys deployed on the appropriate login nodes to allow for passwordless login.
+The SSH plugins allow one to manage which key (and passphrase) to use with which system.
+The keys on Jenkins VM are located under Jenkins home directory (by default \texttt{/var/lib/jenkins/.ssh}.
+Although configuring all of these could be somewhat tedious, once everything is set Jenkins should be able to run scripts on the intended HPC systems via SSH.
+For testing our setup, we created simple Jenkins projects whose task is to print out the \texttt{\$HOSTNAME} of the system.
+
+The drawback of this method is that one has to manage almost all data management explicitly.
+If one checks out or clones a repository on Jenkins (part of Jenkins core feature), it need to be explicitly copied (e.g.
+with \texttt{rsync} or \texttt{scp}) to the remote system.
+Any files generated by the tests that need to be read by Jenkins (e.g.
+plot file) needs to be copied back explicitly to the Jenkins VM.
+A related drawback is that one must explicitly ensure that the build environment is ''clean`` on the remote system (e.g.
+no left over files or data from previous run).
+This is because although Jenkins can clean up its workspace, this workspace (in Jenkins perspective) exists only on the VM.
+The remote systems' workspaces are out of reach from Jenkins.
+This drawback also prevents one to easily allow concurrent builds of the same project.
+
+%\subsection{Master-Node Configuration}
+%We added a standard user account to our cluster that will execute the Jenkins tests.
 Unique ssh keys were generated on the Jenkins Server for accessing the user account on production and test environments.
@@
 
-\subsection{Accessing Login Nodes}
-The ssh public key generated on Jenkins Server was deployed in the login node user account. The login node sshd_config was modified to allow Public Key Authentication from the Jenkins Server IP.
+%\subsection{Accessing Login Nodes}
+%The ssh public key generated on Jenkins Server was deployed in the login node user account. The login node sshd_config was modified to allow Public Key Authentication from the Jenkins Server IP.
 

### 2017-03-24 manuscript/manuscript.tex
Minor headings restructuring. Also a work in progress for the HTTPD section.

@@
 
+\subsection{Installation}
 Jenkins is typically available from the package repository of most major linux distribution of choice.
@@
 
+\subsection{Accessing HPC Test Systems}
 Jenkins has an implicit assumption that the machine on which it is installed is also the primary machine being used to build and test the software.
@@
 
-\subsection{Using Nodes for Test Systems}
+\subsubsection{Using Nodes for Test Systems}
 The original idea behind adding nodes is to allow Jenkins to scale with the workload it has to do.
@@
 
-\subsection{Using SSH Plugins for Test Systems}
+\subsubsection{Using SSH Plugins for Test Systems}
 The SSH plugin (FIXME: Need references) is another method for which one can access the HPC systems from Jenkins.
@@
 %The ssh public key generated on Jenkins Server was deployed in the login node user account. The login node sshd_config was modified to allow Public Key Authentication from the Jenkins Server IP.
+
+\subsection{Securing Jenkins Web Front-end}
+
+Jenkins comes with its own web server.
+Although Jenkins also has a command-line interface, the primary way to interact with Jenkins (configuring, setting up projects, running builds) is via a web browser.
+Although Jenkins web server may be sufficient for a setup in which Jenkins is only accessible in a secure, walled of, intranet environment, we feel that using a more secure, well-tested, production quality web server as its front end is warranted.
+
+We decided to use Apache HTTPD Server as the front-end web server facing the world.
+To achieve that, first we set Jenkins web server to only listen to \texttt{localhost} interface on port 8080, by setting the following variable in Jenkins configuration file \texttt{/etc/sysconfig/jenkins}:
+FIXME: COPY RELEvANT JENKINS CONFIG HERE
+
+Second, we need to forward all HTTP requests to Jenkins, and also forward Jenkins responses back to the client. This is a feature called ''ReverseProxy`` in Apache HTTPD. Th
 

### 2017-04-02 manuscript/manuscript.tex
Removed SWTools section.

--- 2017-03-23 manuscript/manuscript.tex
@@
 \begin{abstract}
-This paper will explore the challenges of regression testing and monitoring of large scale systems such as NCSA’s Blue Waters.
+This paper explores the challenges of regression testing and monitoring of large scale systems such as NCSA's Blue Waters. 
 Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance. 
@@
 We utilize these plots to track trends and alert us to system-level issues before they are reported by our partners (users). 
-Not only does Jenkins have the ability to store historical data, but it can also send email or text pages based on results of a test.
-Other requirements we had include two-factor authentication for accessing the Jenkins GUI with administrator privileges and account management through LDAP.
+Not only does Jenkins have the ability to store historical data, but it can also send email or text messages based on results of a test. 
+Other requirements we had included two-factor authentication for accessing the Jenkins GUI with administrator privileges and account management through LDAP. 
 In this paper we describe our experience in deploying Jenkins as a user-level system-wide regression testing and monitoring framework for Blue Waters.
@@
 
-\begin{abstract}
-LONG-This paper will explore the challenges of regression testing and monitoring of large scale systems such as NCSA’s Blue Waters.
-Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance.
-Another requirement was to find an automated solution for running a suite of test jobs that reveal the system health after upgrades and outages before returning the system to service.
-We evaluated test frameworks such as Inca [1] and Jenkins [2].
-Jenkins was chosen for its versatility, large user base, and multitude of plugins including plotting test results over time.
-We utilize these plots to track trends and alert us to system-level issues before they are reported by our partners (users).
-Not only does Jenkins have the ability to store historical data but it can also send customized notifications (e.g.
-send email or text pages) based on the result of a test.
-Some of the requirements we had include two-factor authentication to access Jenkins GUI with privileges to execute tests and account management through LDAP.
-In this paper we describe our implementation of these requirements to ensure a secure and usable deployment of a Jenkins instance.
+%\begin{abstract}
+%LONG-This paper will explore the challenges of regression testing and monitoring of large scale systems such as NCSA’s Blue Waters. 
+%Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance. 
+%Another requirement was to find an automated solution for running a suite of test jobs that reveal the system health after upgrades and outages before returning the system to service. 
+%We evaluated test frameworks such as Inca [1] and Jenkins [2]. 
+%Jenkins was chosen for its versatility, large user base, and multitude of plugins including plotting test results over time. 
+%We utilize these plots to track trends and alert us to system-level issues before they are reported by our partners (users). 
+%Not only does Jenkins have the ability to store historical data but it can also send customized notifications (e.g. send email or text pages) based on the result of a test. 
+%Some of the requirements we had include two-factor authentication to access Jenkins GUI with privileges to execute tests and account management through LDAP. 
+%In this paper we describe our implementation of these requirements to ensure a secure and usable deployment of a Jenkins instance.
 
-Our Jenkins instance was deployed on a vSphere managed VM running Centos 6.8.
-Security was of the highest concern since Jenkins has the ability to execute commands on our login nodes.
-Jenkins is set to log in as a standard user account with password-less access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM.
-The VM (bwjenkins) was closely vetted by our security team on our test and development system (TDS) before it was allowed access to Blue Waters.
-Iptables was used to lock bwjenkins down to a small internal ip space to ensure the highest security.
-An anonymous user account was enabled with ‘read-only’ access to view current and historical test results.
-During a test, Jenkins downloads software, builds the software, submits a job, awaits completion, gathers and plots the results or returns error information during a failure.
-These are full end to end functionality tests of the programming environment, queueing system, license servers and they provide historical metrics to quickly detect regressions.
+%Our Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. 
+%Security was of the highest concern since Jenkins has the ability to execute commands on our login nodes. 
+%Jenkins is set to log in as a standard user account with password-less access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. 
+%The VM (bwjenkins) was closely vetted by our security team on our test and development system (TDS) before it was allowed access to Blue Waters. 
+%Iptables was used to lock bwjenkins down to a small internal ip space to ensure the highest security. 
+%An anonymous user account was enabled with ‘read-only’ access to view current and historical test results. 
+%During a test, Jenkins downloads software, builds the software, submits a job, awaits completion, gathers and plots the results or returns error information during a failure. 
+%These are full end to end functionality tests of the programming environment, queueing system, license servers and they provide historical metrics to quickly detect regressions.
 
-In this paper we describe in detail our challenges and experiences in deploying Jenkins as a user-level system-wide regression testing and monitoring framework for Blue Waters.
-We will also show some application-based system-level tests we have implemented in Jenkins and share results of those tests.
-The deployment of Jenkins allows us to monitor and detect issues as early as possible from the perspective of a user on Blue Waters, eventually providing a more efficient service for better user experience.
-\end{abstract}
+%In this paper we describe in detail our challenges and experiences in deploying Jenkins as a user-level system-wide regression testing and monitoring framework for Blue Waters. 
+%We will also show some application-based system-level tests we have implemented in Jenkins and share results of those tests. 
+%The deployment of Jenkins allows us to monitor and detect issues as early as possible from the perspective of a user on Blue Waters, eventually providing a more efficient service for better user experience.
+%\end{abstract}
 
@@
 Monitoring large and complex high-performance computing systems has many challenges. 
-Layers and multiple versions of software stack, system-level configurations, (parallel) file systems, diversity in users need and usage, and variable network traffics all interact to increase the system's complexity.
+Layers and multiple versions of the software stack, system-level configurations, (parallel) file systems, diversity in user need and usage, and variable network traffic all interact to increase the system's complexity.
 Although there exist monitoring systems for each of these components, they often do not capture the behavior of the system in aggregate, which in fact is what users and their applications experience. 
-Therefore an application-level system monitoring is needed to give us a more complete picture of the system behavior.
+Therefore an application-level system monitoring framework is needed to give us a more complete picture of the system behavior.
 
-Over time, either due to configuration changes or hardware aging, performance of such complex system may regress.
+Over time, either due to configuration and software changes or hardware aging, performance of such complex system may regress. 
 To identify and correct such regression, one must have some method to do regression testing of the system performance. 
-This requires systematic record of the the system performance over time.
+This requires a systematic record of the system performance over time.
 
-These two requirements can be concisely summarized as an ``application-level regression testing''.
-Our goal was then to come up with an automated solution for running these user-level regression tests to evaluate system usability and performance.
+These two requirements can be concisely summarized as ``application-level regression testing''. 
+Our goal was to implement an automated solution for running these user-level regression tests to evaluate system usability and performance. 
 For this purpose we have chosen to use Jenkins\footnote{http://jenkins.io}.
@@
 Jenkins is an open source automation server. 
-Although it is typically used as continuous integration tool in software development process, its wide-ranging features makes it suitable for any task that can be automated.
+Although it is typically used as a continuous integration tool in the software development process, its wide-ranging features makes it suitable for any task that can be automated. 
 These tasks may include building applications, executing them, deploying software, and running various custom-written tests and scripts. 
-We chose Jenkins as the tool for our regression testing framework because its active development, wide community support, and the readily available ``plugins'' to perform various specific tasks.
+We chose Jenkins as the tool for our regression testing framework because of its active development, wide community support, and the readily available ``plugins'' to perform various specific tasks.
 
-In this paper we describe in details our experience in using Jenkins to perform application-level regression testing on high-performance computing systems such as the Blue Water supercomputer at the National Center for Supercomputing Application, Darter and Beacon at the National Institute for Computational Sciences (NICS).
-These systems are Cray XK, XC, and CS series.
+In this paper we describe in detail our experience in using Jenkins to perform application-level regression testing on high-performance computing systems such as the Blue Water supercomputer at the National Center for Supercomputing Applications (NCSA), Darter and Beacon at the National Institute for Computational Sciences (NICS).
+These systems are Cray XE, XK, XC, and CS series. 
 The outline of this paper is as follows. 
-[FIXME: WRITE PAPER OUTLINE AFTER COMPLETE DRAFT]
-
-%Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance.
-Another requirement was to find an automated solution for running a suite of test jobs that reveal the system health after upgrades and outages before returning the system to service.
+[FIXME: WRITE PAPER OUTLINE AFTER COMPLETE DRAFT].
 
@@
 
-% \subsection{Introduction to Jenkins}
-% Jenkins [2] is a self-contained, open source automation server which can be used to automate all sorts of tasks such as building, testing, and deploying software.
-Jenkins can be installed through native system packages, Docker, or even run standalone by any machine with the Java Runtime Environment installed.
-% To install from rpm as root for centos:
-% \begin{lstlisting}
-% wget -O /etc/yum.repos.d/jenkins.repo \
-%   http://pkg.jenkins-ci.org/redhat-stable/jenkins.repo
-% rpm --import \
-%   https://jenkins-ci.org/redhat-stable/jenkins-ci.org.key
-% yum install jenkins
-% \end{lstlisting}
-
-Jenkins is typically available from the package repository of most major linux distribution of choice.
+\subsection{Installation}
+Jenkins is typically available from the package repository of most major linux distributions. 
 One can also download and install Jenkins directly from its website. 
@@
 Jenkins comes with its own web server so that managing and accessing Jenkins can be done via any web browser (in the next section we discuss using Apache HTTP Server in front of Jenkin's for better security).
-Typically Jenkins's web server listen to port 8080, but this is configurable.
+Typically Jenkins's web server listens on port 8080, but this is configurable.
 
+\subsection{Accessing HPC Test Systems}
 Jenkins has an implicit assumption that the machine on which it is installed is also the primary machine being used to build and test the software. 
-In our case, this is not what we would want.
+In our case, this is not what we want. 
 In fact, our applications will be built on the HPC system on which we intent to run the tests (typically on the login nodes), and will be run on the compute nodes of the HPC system (i.e.
 via batch job submission to the job queueing system).
-This is because not only we want to test the runtime performance of the applications, but also we want to ensure that the software and programming environment of the system can still build the applications correctly.
-Incidentally, the latter also informs us any user-level problem such as slow or overloaded login nodes, slow file system access, erroneous or incompatible default software (library, compilers, etc) versions.
-In short, we want our tests to simulate typical workflow of a user on the system being testing.
+This is because not only do we want to test the runtime performance of the applications, but we also want to ensure that the software and programming environment of the system can build the applications correctly.
+Incidentally, the latter also informs us of any user-level problem such as slow or overloaded login nodes, slow file system access, erroneous or incompatible default software (library, compilers, etc) versions.
+In short, we want our tests to simulate the typical workflow of a user on the system being tested.
 
@@
 It also provides the user interface (via its own web server) to create and configure projects. 
-These tasks are sufficiently light weight such that Jenkins can be installed on a VM with sufficient disk space for the artifacts, since the trully heavy lifting on building and executing the application tests are done on the remote machine.
+These tasks are sufficiently light weight that Jenkins can be installed on a VM with sufficient disk space for the artifacts, since the truly heavy lifting on building and executing the application tests are done on the remote machine.
 
-There are two ways to achieve executing builds on remote machine.
-Each has their own benefits, and whichever way to use is a matter of choice.
+There are two ways to achieve an executing build on a remote machine. 
+Each have their own benefits, and your selection is a matter of choice. 
 One may use Jenkin's core feature of adding ``Nodes`` to its environment. 
-One may also use a Jenkins plugin called ''SSH Plugin`` to allow execution on remote machine via SSH protocol.
+One may also use a Jenkins plugin called ''SSH Plugin`` to allow execution on a remote machine via SSH protocol. 
 At NICS our setup uses the former, while at NCSA our setup uses the latter. 
@@
 
-\subsection{Using Nodes for Test Systems}
+\subsubsection{Using Nodes for Test Systems}
 The original idea behind adding nodes is to allow Jenkins to scale with the workload it has to do. 
-As projects are added, one can add nodes (i.e.
-more build machines) allowing Jenkins to build more projects concurrently.
-Jenkin's project can also be explicitly 'labeled' to only be executed on a certain node.
+As projects are added, one can add nodes (i.e. more build machines) allowing Jenkins to build more projects concurrently. 
+Jenkin's projects may also be explicitly 'labeled' to execute on a certain node. 
 We capitalized both of these features to enable the aforementioned remote execution.
@@
 For each HPC system login node, we created a Jenkins node\footnote{Do not be confused with multiple usage of the word ''node`` here. 
-The former refers to the typical usage of login node in HPC.
+The former refers to the typical usage of a login node in HPC. 
 The latter refers to Jenkins' vernacular of ''node`` as previously defined}. 
@@
 For example, at NICS we have the labels 'beacon' and 'darter' to refer to the Cray CS-300 (Beacon) and XC-30 (Darter) login nodes, respectively. 
-Each test application (i.e.
-''project``) is then labeled to ensure that they only run on the appropriate node.
-For example, we have used NAMD (FIXME: Need reference for NAMD) as an applicaton test.
-We would create a Jenkin project called ''NAMD-Beacon`` and label it to only run on ''beacon`` node.
+Each test application (i.e. ''project``) is then labeled to ensure that they only run on the appropriate node. 
+For example, we have used NAMD (FIXME: Need reference for NAMD) as an application test. 
+We would create a Jenkins project called ''NAMD-Beacon`` and label it to run only on the ''beacon`` node. 
 We would also create another project called ''NAMD-Darter`` and label it appropriately. 
-The two projects have slighly different build scripts (and possibly different test cases) so that they build correctly on the systems they were meant to run on.
+The two projects have slightly different build scripts (and possibly different test cases) so that they build correctly on the systems where they were meant to run.
 
-Jenkins nodes need to have a Java-based daemon (Jenkins' ''slave.jar``) to run which connect back to the master via a certain port (which is configurable).
+Jenkins nodes need to have a Java-based daemon (Jenkins' ''slave.jar``) to run which connects back to the master via a certain port (which is configurable). 
 This can be considered a drawback. 
 If the daemon somehow dies, it needs to be restarted. 
-The daemon runs as regular user, the user which essentially runs the build and submit the jobs on the HPC system.
-In our case, we created a user called ''jenkins`` with the same privilege as any other regular user.
-Both the extra port opening and the daemon itself may be considered as attack vectors from security perspective.
-At NICS however we consider this to be acceptable because of other mitigation (which we will discussed later).
+The daemon runs as regular user, the user which essentially runs the build and submits the jobs on the HPC system. 
+In our case, we created a NICS user called ''jenkins`` with the same privilege as any other regular user. 
+Both the extra port opening and the daemon itself may be considered as attack vectors from a security perspective. 
+At NICS however we consider this to be acceptable because of other mitigation (which we will discuss later).
 
-The benefit of this method is that one can basically treat the nodes as local environment in Jenkins, while having access to the HPC environment.
+The benefit of this method is that one can basically treat the nodes as a local environment in Jenkins, while having access to the HPC environment. 
 For example, each node would have access to the parallel lustre filesystem mounted by the HPC system (even if Jenkins master itself does not, being only a small separate VM). 
@@
 Yet Jenkins automatically manages all communication with the nodes such that files (e.g.
-plot data, test output) generated on the lustre filesystem is readable from Jenkins without the explicit remote copy (i.e.
+plot data, test output) generated on the lustre filesystem are readable from Jenkins without the explicit remote copy (i.e.
 via SCP).
-Another example is that one can have Jenkins checkout or clone code from remote repository (e.g.
+Another example is that one can have Jenkins checkout or clone code from remote a repository (e.g.
 using Subversion or Git) and the copy will be automatically available on the lustre filesystem defined as the workspace of that node.
-These benefits integration makes building Jenkins project more seamless.
+These integration benefits make building Jenkins projects more seamless.
 
-\subsection{Master-Node Configuration}
-We added a standard user account to our cluster that will execute the Jenkins tests.
-Unique ssh keys were generated on the Jenkins Server for accessing the user account on production and test environments.
-The keys on the server are located in Jenkins home directory (/var/lib/jenkins/.ssh).
-Using the GUI management console, the keyfile location and passphrase was entered under Manage Jenkins, Configure System, SSH remote hosts section.
-A unique SSH site is configured for our TDS, production and development login nodes.
+\subsubsection{Using SSH Plugins for Test Systems}
+The SSH plugin (FIXME: Need references) is another method for which one can access the HPC systems from Jenkins. 
+As the name implies, Jenkins projects with these type of build scripts simply SSH to the desired machine then execute the scripts there.
 
-\subsection{Accessing Login Nodes}
-The ssh public key generated on Jenkins Server was deployed in the login node user account. The login node sshd_config was modified to allow Public Key Authentication from the Jenkins Server IP.
+The benefit of this method is that it more closely mimicks the way real users access the HPC system. 
+There is no need for an additional daemon to run on the HPC login nodes and there is no need for the corresponding opening of a port on the Jenkins VM. 
+Because NCSA and NICS systems utilize two-factor RSA one-time password for user login, one must make a slight modification so that Jenkins can have automated logins. 
+The NCSA login node's \texttt{/etc/ssh/sshd_config} was modified to allow ''Public Key Authentication`` from the Jenkins VM unique IP address. 
+We created an NCSA user called ''bwjenkins`` with standard user privilege. 
+Pairs of SSH keys with passphrase were generated on the Jenkins VM with their public keys deployed on the appropriate login nodes in the bwjenkins user account to allow passwordless login. 
+The SSH plugins allow one to manage which key (and passphrase) to use with which system. 
+The keys on the Jenkins VM are located under the Jenkins home directory (by default \texttt{/var/lib/jenkins/.ssh}. 
+Although this configuration can be somewhat tedious, when complete, Jenkins will be able to run scripts on the intended HPC systems via SSH. 
+For testing our setup, we created simple Jenkins projects whose task is to print out the \texttt{\$HOSTNAME} of the system.
 
-\section{Authentication and Authorization}
-\label{sec:AuthenticationAuthorization}
+The drawback of this method is that one has to manage almost all data management explicitly. 
+If one checks out or clones a repository on Jenkins (part of Jenkins core feature), it needs to be explicitly copied (e.g. with \texttt{rsync} or \texttt{scp}) to the remote system. 
+Any files generated by the tests that need to be read by Jenkins (e.g. plot file) have to be copied back explicitly to the Jenkins VM. 
+A related drawback is that one must explicitly ensure that the build environment is ''clean`` on the remote system (e.g. no left over files or data from previous run). 
+This is because although Jenkins can clean up its workspace, this workspace (in Jenkins perspective) exists only on the VM. 
+The remote systems' workspaces are out of the reach of Jenkins. 
+This drawback also prevents one to easily allow concurrent builds of the same project.
 
-\subsection{Security Considerations}
-Enabling Jenkins access to Blue Waters posed some unique security hurdles that we had to overcome.
-Blue Waters is an OTP only restricted access system.
-Jenkins has the ability to execute user-level commands on our login nodes.
-Jenkins has some unfortunate default settings.
-The access control is set to "Jenkins' own user database," and the "Allow users to sign up" option is enabled, so if you don't have an account, you can create one by providing your name, e-mail and a password.
-Additionally, there's an authorization option enabled which says "Logged-in users can do anything." So, once signed in, you have full admin access to the Jenkins system instance.
-This required us initially to test the deployment with our test and development (TDS) CRAY.
-This resulted in the following requirement: restricted OTP access to the physical system hosting Jenkins.
-In addition, OTP only access to the Jenkins GUI command console must be contained within our IP space.
-The Jenkins GUI will also restrict the command console access to our Blue Waters LDAP server.
+\subsection{Securing Jenkins Web Front-end}
 
-\subsection{Configuration Choices}
-The Jenkins instance was deployed on a vSphere managed VM running Centos 6.8.
-The VM allows restricted host-based ssh access from two secure OTP only administrative systems.
-The Jenkins GUI presented additional challenges.
-The Jenkins GUI is configured to log in as a standard user account with password-less access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM.
-We restrict access to the physical VM (bwjenkins) and the Jenkins GUI utilizing iptables, SSL and OTP.
-A reverse proxy was used to run Jenkins behind apache/http with SSL for access to the administrative console.
-All the configuration is in /etc/httpd/conf.d/ssl.conf.
-Anonymous access to the Jenkins GUI was allowed for limited read only view of test status and historical plots.
-The Anonymous access view is not restricted.
+Jenkins comes with its own web server. 
+Although Jenkins also has a command-line interface, the primary way to interact with Jenkins (configuring, setting up projects, running builds) is via a web browser. 
+Although the Jenkins web server may be sufficient for a setup in which Jenkins is only accessible in a secure, walled off, intranet environment, we feel that using a more secure, well-tested, production quality web server as its front end is warranted.
+
+We decided to use an Apache HTTP Server as the front-end web server facing the world. 
+To achieve that, first we set the Jenkins web server to only listen to the \texttt{localhost} interface on port 8080, by setting the following variable in Jenkins configuration file \texttt{/etc/sysconfig/jenkins}:
+\begin{lstlisting}
+#-- Restrict to only listen to localhost
+JENKINS_PORT="8080"
+JENKINS_LISTEN_ADDRESS=127.0.0.1
+\end{lstlisting}
+
+Second, we need to forward all HTTP requests to Jenkins, and also forward Jenkins responses back to the client. 
+This is accomplished using the module \texttt{mod_proxy} (FIXME: Add Reference) in Apache HTTP which allows it to act as a proxy / gateway. 
+To enable this feature, the following stanza is added to the configuration file \texttt{/etc/httpd/conf.d/ssl.conf} inside the \texttt{<VirtualHost>} directive:
 
 \begin{lstlisting}
-(Jenkins sever configuration file snippets below)
-/etc/ssh/sshd_config:
-Match Host bwbh1.ncsa.illinois.edu,
-bwbh2.ncsa.illinois.edu
-HostbasedAuthentication yes
-
-/etc/sysconfig/iptables:
--A INPUT -s 141.142.0.0/16 -m state --state NEW -m tcp 
--p tcp --dport 22 -j ACCEPT
--A INPUT -s 172.16.0.0/15 -m state --state NEW -m tcp 
--p tcp --dport 22 -j ACCEPT *delete maybe*
--A INPUT  -m state --state NEW -m tcp -p tcp --dport 80 
--j ACCEPT
--A INPUT -s 141.142.0.0/16 -m state --state NEW -m tcp 
--p tcp --dport 443 -j ACCEPT
-
-/etc/httpd/conf.d/ssl.conf:
- # -- The following sets ReverseProxy for Jenkins
 ProxyRequests       Off
@@
 RequestHeader set X-Forwarded-Port "443"    
+\end{lstlisting}
 
- # -- The following sets OTP for Jenkins SSL connection
-  DefineExternalAuth pwauth+session pipe /usr/local/bin/
-  pwauth+session
+With this setup, all requests to the HTTP over SSL protocol (i.e.
+\texttt{https}) on port 443 by default) are forwarded to the Jenkins server and Jenkins responses are forwarded back to the client (i.e.
+web browser).
+
+Optionally, one may allow non-authenticated, ''read-only`` access to the Jenkins dashboard over regular (non-secure) HTTP connections. 
+Jenkins' own authorization mechanism can be used to control this access, but we can also add Apache HTTP directives for further security, limiting \texttt{GET} requests. 
+To achieve this, we created the file \texttt{/etc/httpd/conf.d/vhosts.conf} with the following content:
+\begin{lstlisting}
+
+NameVirtualHost *:80
+<VirtualHost *:80>
+
+  ServerAdmin tbouvet@illinois.edu
+  DocumentRoot /var/www/html
+  ServerName bwjenkins.ncsa.illinois.edu
+  Options Indexes FollowSymLinks
+
+  ProxyPass / http://localhost:8080/ nocanon
+  ProxyPassReverse  /  http://localhost:8080/
+  ProxyRequests Off
+  AllowEncodedSlashes On
+
+  LimitRequestBody 512
+  LimitRequestFields 15
+  LimitRequestFieldSize 1024
+  LimitRequestLine 128
+
+  <Location /asynchPeople/>
+    Order Deny,Allow
+    Deny from all
+  </Location>
+
+  <Proxy *>
+    Order deny,allow
+    Allow from all
+    <LimitExcept GET>
+      Deny from all
+    </LimitExcept>
+  </Proxy>
+
+</VirtualHost>
+
+\end{lstlisting}
+
+\subsection{Authenticating with One-Time Password}
+
+Although Jenkins supplies its own authentication mechanism with its built-in user and password database, we feel that it is inadequate for securing our instance. 
+The default Jenkins authentication setup is also unfortunate, in which it allows anyone to self-register creating their own username and password \footnote{This is perhaps another artifact of Jenkins setup intended to intranet environment.}
+We wanted instead to use our One-Time Password (OTP) infrastructure with RSA SecurID (FIXME: Add references https://www.rsa.com/en-us/products/rsa-securid-suite, https://en.wikipedia.org/wiki/RSA_SecurID) token for authentication.
+In this section we describe how we accomplished that.
+
+Our use of Apache HTTP Server as front-end allow us to use ''Basic Authentication`` (FIXME: Add Reference).
+Via \texttt{mod_authnz_external} module, one can use any external mechanism or program to authenticate.
+One example of an authenticator is the ''pwauth`` authentication program. 
+It is a simple program that returns a status code given a login (username) and password.
+
+Combined with the Pluggable Authentication Module (PAM) --- a Unix authentication framework ---, we use ''pwauth`` to authenticate against our RSA SecurID OTP infrastructure. 
+This is set up in the file \texttt{/etc/pam.d/pwauth}:
+\begin{lstlisting}
+#%PAM-1.0
+auth	   required	/lib64/security/pam_securid.so
+account    include      password-auth
+\end{lstlisting}
+
+Jenkins can use the user information given by Apache HTTP server if one selects ''HTTP Header by reverse proxy`` for its security realm. 
+This means that all authentication is handled by Apache. 
+Authenticating directly to \texttt{pwauth} against RSA SecurID OTP however presents an issue. 
+It is often the case that a request needs to re-authenticate. 
+The web browser normally handles this seamlessly by caching the user's credentials.
+However, this does not work since, by definition, OTP credentials can only be used once. 
+The solution is to use a back-end authenticator with some form of session management.
+
+To accomplish this, we wrote a small python script called ''BasicAuthOTPSession`` [FIXME: Add Reference] as the authentication mechanism, wrapping the real authenticator (i.e.
+\texttt{pwauth} with PAM for RSA SecurID in our case).
+For the first time, it calls the real authenticator. 
+Once an authentication succeed, a session is created and the next request with the same credentials from the same IP address are deemed successful without going through the real authenticator. 
+The session expires in a predefined amount of time. 
+A new request within that time renew the session. 
+If there is no more request within that time, the session expires.
+When this happens, one has to authenticate again with the real authenticator.
+
+Figure {FIXME: CREATE FIGURE) illustrates the authentication mechanism we describe. 
+Most of the configuration is defined in the file \texttt{/etc/httpd/conf.d/ssl.conf}, immediately following listing [FIXME: CITE LISTING] inside the same \texttt{<VirtualHost>} directive:
+
+\begin{lstlisting}
+#-- OTP for Jenkins SSL connection
+DefineExternalAuth pwauth+session pipe 
+  /usr/local/bin/BasicAuthOTPSession.py
+
 <LocationMatch / > 
@@
   require valid-user  
-
   RequestHeader unset "X-Forwarded-User"
   RequestHeader set "X-Forwarded-User" (REMOTE_USER)
-
 </LocationMatch>
 
- /usr/local/bin/pwauth+session: https://github.com/reubendb/
- BasicAuthOTPSession/blob/master/BasicAuthOTPSession.py#L1
 \end{lstlisting}
-\subsection{LDAP with Jenkins}
-\begin{figure}[H]
+The \texttt{<LocationMatch / >} directive ensures that every request to the secure HTTP site is authenticated.
+
+\subsection{Authorization and Access Control}
+\label{subsec:authorization}
+
+Jenkins default authorization allows logged in (authenticated) users to have full control. 
+We wanted a more fine-grained access control to our instance and therefore selected the ''matrix-based security`` option (see Figure \ref{fig:jenkinsAuthorization}).
+Using this option we can limit what access individual users and groups have to our Jenkins instance.
+For example we restrict most users (other than admin users) from having the ''Job Delete`` permission to prevent one user or group from deleting each other's jobs.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\textwidth]{Configure-Global-Security}
+\caption{Jenkins fine-grained authorization.}
+\label{fig:jenkinsAuthorization}
+\end{figure}
+
+We use the built-in LDAP plugin to query our LDAP server what group a user belongs to.
+This greatly simplifies managing the authorization since it can be done based on groups rather than just individual users. 
+The LDAP plugins gets the user information from the HTTP header passed by the reverse proxy set up. 
+Figure \ref{fig:LDAP-Jenkins} shows the screenshot of our LDAP configuration within Jenkins interface.
+
+\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
-\caption{ Use LDAP with Jenkins }
+\caption{Using LDAP with Jenkins.}
 \label{fig:LDAP-Jenkins}
 \end{figure}
-To enable LDAP, the LDAP Plugin was installed.
-To configure, from the console view, select Manage Jenkins, then select Configure Global Security.
-In the Security Realm section select the Advanced...
-tab.
-Input your LDAP server name and root DN.
-Click the Test Button.\\
-\\
-My first stab at this failed as an anonymous connection to our LDAP because we are using a local CA.
-WARNING: Failed to search LDAP for username, 
-sun.security.provider.certpath.SunCertPathBuilderException:
-unable to find valid certification path to requested target\\
-\\
-We had to add our certificate to the keystore:
-/usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
-Enter keystore password: Trust this certificate? [no]:  yes\\
-Certificate was added to keystore
 
-\subsection{Configure Global Security}
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.5\textwidth]{Configure-Global-Security}
-\caption{ Configure Global Security }
-\label{fig:Configure-Global-Security}
-\end{figure}
-We are allowing access by username and LDAP groups.
-The permissions can be scoped for individuals and groups.
-An example is removing Job delete permissions to prevent one user or group from deleting each other's jobs.
+Since Jenkins allows one to enter arbitrarily command to be executed on login nodes, we want to further mitigate security risk via firewall rules. 
+In our installation, we only allow IP address originating from our institution block to access the secure HTTP portion and authenticate to access Jenkins. 
+At NCSA, the non secure, read-only, HTTP portion is accessible from anywhere. 
+At NICS, this access is only allowed from the institution IP block only.
+
+%/etc/sysconfig/iptables:
+%-A INPUT -s 141.142.0.0/16 -m state --state NEW -m tcp 
+%-p tcp --dport 22 -j ACCEPT
+%-A INPUT -s 172.16.0.0/15 -m state --state NEW -m tcp 
+%-p tcp --dport 22 -j ACCEPT 
+%-A INPUT -m state --state NEW -m tcp -p tcp --dport 80 
+%-j ACCEPT
+%-A INPUT -s 141.142.0.0/16 -m state --state NEW -m tcp 
+%-p tcp --dport 443 -j ACCEPT
 
@@
  We retroactively modified all tests to limit the number of old build logs retained (max 50 for most tests).
+
 \subsection{ssh to a login host}
@@
 
-\section{SWTools Integration}
-\label{sec:SWToolsIntegration}
-\subsection{SWTools with Jenkins}
-%\begin{figure}[H]
-%\centering
-%\includegraphics[width=0.5\textwidth]{swtools-Jenkins}
-%\caption{ Use SWTools with Jenkins }
-%\label{fig:swtools-jenkins}
-%\end{figure}
-
-\subsection{SWTools with Lammps}
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.5\textwidth]{swtools-lammps}
-\caption{ SWTools with Lammps }
-\label{fig:swtools-lammps}
-\end{figure}
-
 \section{Use Cases}
@@
  One of our best practices is to provide a management level summary description for casual jenkins users who want to view the tests but do not need to understand the full Jenkins configuration and execution details.
+
 \begin{figure}[H]
@@
  Where scripts on the remote SSH site are used, they are echoed and/or displayed with "cat -n" to make console output verbose and easy to debug in case of errors.
+
 \begin{figure}[H]
@@
 \section{Conclusion}
+\label{sec:conclusion}
+
+We typically run the latest Programming Environment (PE) on our TDS.
+Our production login nodes and the supercomputer have the latest PE installed as non default during initial testing and it can be loaded by modulefile selection.
+Our test login node (Bright Cluster Provisioned EsLogin) is utilized for testing new software stacks and changes to the login environment that are independent of our production resources.
+Therefore Jenkins Projects tailored for each environment allow for regression testing of the current production as well as pre-production user-level environments.
+
 \subsection{reproducibility and regression testing}
@@
 This is the primary reason we require peer review for new tests.
-\label{sec:conclusion}
 
@@
 \section*{References}
-[1] http://inca.sdsc.edu/ Inca Monitoring: periodic, automated, user-level cyberinfrastructure testing
-[2] https://jenkins.io/ Jenkins: open source automation server written in Java
+%[1] http://inca.sdsc.edu/ Inca Monitoring: periodic, automated, user-level cyberinfrastructure testing
+[1] https://jenkins.io/ Jenkins: open source automation server written in Java
 

### 2017-04-04 manuscript/manuscript.tex
Reworked abstract.

@@
 \begin{abstract}
-This paper explores the challenges of regression testing and monitoring of large scale systems such as NCSA's Blue Waters. 
+Monitoring and testing for regression of large scale systems such as the NCSA's Blue Waters supercompuer are challenging task. 
+In this paper we describe the solution we came up with to perform those tasks. 
 Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance.
-Jenkins was chosen for its versatility, large user base, and multitudes of plugins including plotting test results over time. 
-We utilize these plots to track trends and alert us to system-level issues before they are reported by our partners (users). 
-Not only does Jenkins have the ability to store historical data, but it can also send email or text messages based on results of a test. 
-Other requirements we had included two-factor authentication for accessing the Jenkins GUI with administrator privileges and account management through LDAP. 
-In this paper we describe our experience in deploying Jenkins as a user-level system-wide regression testing and monitoring framework for Blue Waters.
+Jenkins, an automation server software, was chosen for its versatility, large user base, and multitudes of plugins including collecting data and plotting test results over time. 
+We describe our Jenkins deployment to launch and monitor jobs on remote HPC system, perform authentication with one-time password, and integrate with our LDAP server for its authorization. 
+We show some use cases and describe our best practices for successfully using Jenkins as a user-level system-wide regression testing and monitoring framework for Blue Waters.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Performance; Benchmarking; Computer architecture
+System-monitoring; Regression-testing; Application; Performance; Benchmarking
 \end{IEEEkeywords}
-
-%\begin{abstract}
-%LONG-This paper will explore the challenges of regression testing and monitoring of large scale systems such as NCSA’s Blue Waters. 
-%Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance. 
-%Another requirement was to find an automated solution for running a suite of test jobs that reveal the system health after upgrades and outages before returning the system to service. 
-%We evaluated test frameworks such as Inca [1] and Jenkins [2]. 
-%Jenkins was chosen for its versatility, large user base, and multitude of plugins including plotting test results over time. 
-%We utilize these plots to track trends and alert us to system-level issues before they are reported by our partners (users). 
-%Not only does Jenkins have the ability to store historical data but it can also send customized notifications (e.g. send email or text pages) based on the result of a test. 
-%Some of the requirements we had include two-factor authentication to access Jenkins GUI with privileges to execute tests and account management through LDAP. 
-%In this paper we describe our implementation of these requirements to ensure a secure and usable deployment of a Jenkins instance.
-
-%Our Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. 
-%Security was of the highest concern since Jenkins has the ability to execute commands on our login nodes. 
-%Jenkins is set to log in as a standard user account with password-less access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. 
-%The VM (bwjenkins) was closely vetted by our security team on our test and development system (TDS) before it was allowed access to Blue Waters. 
-%Iptables was used to lock bwjenkins down to a small internal ip space to ensure the highest security. 
-%An anonymous user account was enabled with ‘read-only’ access to view current and historical test results. 
-%During a test, Jenkins downloads software, builds the software, submits a job, awaits completion, gathers and plots the results or returns error information during a failure. 
-%These are full end to end functionality tests of the programming environment, queueing system, license servers and they provide historical metrics to quickly detect regressions.
-
-%In this paper we describe in detail our challenges and experiences in deploying Jenkins as a user-level system-wide regression testing and monitoring framework for Blue Waters. 
-%We will also show some application-based system-level tests we have implemented in Jenkins and share results of those tests. 
-%The deployment of Jenkins allows us to monitor and detect issues as early as possible from the perspective of a user on Blue Waters, eventually providing a more efficient service for better user experience.
-%\end{abstract}
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
 
@@
 
-Monitoring large and complex high-performance computing systems has many challenges. 
+Monitoring large and complex high-performance computing systems have many challenges. 
 Layers and multiple versions of the software stack, system-level configurations, (parallel) file systems, diversity in user need and usage, and variable network traffic all interact to increase the system's complexity.
@@
 via SCP).
-Another example is that one can have Jenkins checkout or clone code from remote a repository (e.g.
+Another example is that one can have Jenkins checkout or clone code from a remote repository (e.g.
 using Subversion or Git) and the copy will be automatically available on the lustre filesystem defined as the workspace of that node.
@@
 Optionally, one may allow non-authenticated, ''read-only`` access to the Jenkins dashboard over regular (non-secure) HTTP connections. 
-Jenkins' own authorization mechanism can be used to control this access, but we can also add Apache HTTP directives for further security, limiting \texttt{GET} requests. 
+Jenkins' own authorization mechanism can be used to control this access, but we can also add Apache HTTP directives for further security, limiting to \texttt{GET} requests only. 
 To achieve this, we created the file \texttt{/etc/httpd/conf.d/vhosts.conf} with the following content:
@@
 
-\subsection{Authenticating with One-Time Password}
+\section{Authenticating with One-Time Password}
 
 Although Jenkins supplies its own authentication mechanism with its built-in user and password database, we feel that it is inadequate for securing our instance. 
-The default Jenkins authentication setup is also unfortunate, in which it allows anyone to self-register creating their own username and password \footnote{This is perhaps another artifact of Jenkins setup intended to intranet environment.}
+The default Jenkins authentication setup is also unfortunate, in which it allows anyone to self-register creating their own username and password\footnote{This is perhaps another artifact of Jenkins setup intended for intranet environment}.
 We wanted instead to use our One-Time Password (OTP) infrastructure with RSA SecurID (FIXME: Add references https://www.rsa.com/en-us/products/rsa-securid-suite, https://en.wikipedia.org/wiki/RSA_SecurID) token for authentication.
@@
 #-- OTP for Jenkins SSL connection
-DefineExternalAuth pwauth+session pipe 
+DefineExternalAuth pwauth+session pipe \
 /usr/local/bin/BasicAuthOTPSession.py
@@
 
-\subsection{Authorization and Access Control}
-\label{subsec:authorization}
+\section{Authentication and Authorization}
+\label{sec:AuthenticationAuthorization}
 
-Jenkins default authorization allows logged in (authenticated) users to have full control. 
-We wanted a more fine-grained access control to our instance and therefore selected the ''matrix-based security`` option (see Figure \ref{fig:jenkinsAuthorization}).
-Using this option we can limit what access individual users and groups have to our Jenkins instance.
-For example we restrict most users (other than admin users) from having the ''Job Delete`` permission to prevent one user or group from deleting each other's jobs.
+%\subsection{Security Considerations}
+%CUT THE NEXT TWO PARAGRAPHS AND DESCRIPTION OF CONFIG FILES OR REDUCE SINCE IT IS COVERED ABOVE --GALEN
+%Enabling Jenkins access to Blue Waters posed some unique security hurdles that we had to overcome. 
+%Blue Waters is an OTP only restricted access system. 
+%Jenkins has the ability to execute user-level commands on our login nodes. 
+%It also has some unfortunate default settings. 
+%The access control is set to "Jenkins' own user database," and the "Allow users to sign up" option is enabled, so if you don't have an account, you can create one by providing your name, e-mail and a password.
+%Additionally, there's an authorization option enabled which says "Logged-in users can do anything." So, once signed in, you have full admin access to the Jenkins system instance. 
+% This required us initially to test the deployment with our TDS. 
+%This resulted in the following requirement: restricted OTP access to the physical system hosting Jenkins. 
+%In addition, OTP only access to the Jenkins GUI command console must be contained within our IP space. 
+% The Jenkins GUI will also restrict the command console access to our Blue Waters LDAP server.
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.5\textwidth]{Configure-Global-Security}
-\caption{Jenkins fine-grained authorization.}
-\label{fig:jenkinsAuthorization}
-\end{figure}
+%\subsection{Configuration Choices}
+%The Jenkins instance was deployed on a vSphere managed VM running Centos 6.8.
+The VM allows restricted host-based ssh access from two secure OTP only administrative systems.
+The Jenkins GUI presented additional challenges.
+The Jenkins GUI is configured to log in as a standard user account with password-less access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM.
+We restrict access to the physical VM (bwjenkins) and the Jenkins GUI utilizing iptables, SSL and OTP.
+Jenkins is configured to listen on port 8080 by default and we restricted it to localhost only.
+A reverse proxy was configured to run Jenkins behind Apache HTTP Server and SSL for access to the administrative console.
+With this reverse proxy, apache accepts requests on port 80 and 443 of bwjenkins.ncsa.illinois.edu and forwards them to the Jenkins web server at localhost which is now firewall protected.
+Most of this configuration is in /etc/httpd/conf.d/ssl.conf.
+Anonymous access to the Jenkins GUI was allowed for limited read only view of test status and historical plots.
+The Anonymous access view is not restricted.
 
-We use the built-in LDAP plugin to query our LDAP server what group a user belongs to.
-This greatly simplifies managing the authorization since it can be done based on groups rather than just individual users. 
-The LDAP plugins gets the user information from the HTTP header passed by the reverse proxy set up. 
-Figure \ref{fig:LDAP-Jenkins} shows the screenshot of our LDAP configuration within Jenkins interface.
+%\begin{lstlisting}
+%NOTE: Install mod_authnz_external Apache package
 
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
-\caption{Using LDAP with Jenkins.}
-\label{fig:LDAP-Jenkins}
-\end{figure}
+%(Jenkins sever configuration file snippets below)
 
-Since Jenkins allows one to enter arbitrarily command to be executed on login nodes, we want to further mitigate security risk via firewall rules. 
-In our installation, we only allow IP address originating from our institution block to access the secure HTTP portion and authenticate to access Jenkins. 
-At NCSA, the non secure, read-only, HTTP portion is accessible from anywhere. 
-At NICS, this access is only allowed from the institution IP block only.
+%/etc/ssh/sshd_config:
+%Match Host bwbh1.ncsa.illinois.edu,
+%bwbh2.ncsa.illinois.edu
+%HostbasedAuthentication yes
 
@@
 
+%/etc/httpd/conf.d/ssl.conf:
+% # -- The following sets ReverseProxy for Jenkins
+%ProxyRequests       Off
+%ProxyPreserveHost   On
+%AllowEncodedSlashes On
+%<Proxy *>
+%Order deny,allow
+%Allow from all
+%</Proxy>
+%ProxyPass       / http://localhost:8080/ nocanon
+%ProxyPassReverse / http://localhost:8080/
+%ProxyPassReverse / http://bwjenkins.ncsa.illinois.edu/
+%RequestHeader set X-Forwarded-Proto "https"
+%RequestHeader set X-Forwarded-Port "443"
+
+%\begin{lstlisting}
+% # -- OTP for Jenkins SSL connection
+%DefineExternalAuth pwauth+session pipe 
+%/usr/local/bin/pwauth+session
+%<LocationMatch / > 
+%AuthType Basic
+%AuthBasicProvider external
+%AuthName "NCSA RSA OTP login" 
+%AuthExternal pwauth+session
+%require valid-user  
+%RequestHeader unset "X-Forwarded-User"
+%RequestHeader set "X-Forwarded-User" (REMOTE_USER)
+%</LocationMatch>
+ %
+%
+%/usr/local/bin/pwauth+session(OTP caching): 
+%https://github.com/reubendb/BasicAuthOTPSession
+%/blob/master/BasicAuthOTPSession.py#L1
+%
+ % 
+%/etc/pam.d/pwauth (for OTP):
+ %#%PAM-1.0
+%auth  required  /lib64/security/pam_securid.so
+%account  include  password-auth
+%\end{lstlisting}
+%/etc/sysconfig/jenkins (restrict to localhost):
+%JENKINS_PORT="8080"
+%JENKINS_LISTEN_ADDRESS=127.0.0.1
+%\end{lstlisting}
+\subsection{LDAP with Jenkins} 
+%To enable LDAP, the LDAP Plugin was installed.
+To configure, from the console view, select Manage Jenkins, then select Configure Global Security.
+In the Security Realm section select the Advanced...
+tab.
+Input your LDAP server name and root DN.
+Click the Test Button.
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
+\caption{ Use LDAP with Jenkins }
+\label{fig:LDAP-Jenkins}
+\end{figure}
+To enable LDAP, the LDAP Plugin was installed.
+To configure, from the console view, select Manage Jenkins, then select Configure Global Security.
+In the Security Realm section select the Advanced...
+tab.
+Input your LDAP server name and root DN.
+Click the Test Button.\\
+At first this failed because our LDAP is using a local CA.
+WARNING: Failed to search LDAP for username, 
+sun.security.provider.certpath.SunCertPathBuilderException:
+unable to find valid certification path to requested target\\
+\\
+We had to add our certificate to the keystore:
+/usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
+Enter keystore password: Trust this certificate? [no]:  yes\\
+Certificate was added to keystore
+
+\subsection{Configure Global Security}
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{Configure-Global-Security}
+\caption{ Configure Global Security }
+\label{fig:Configure-Global-Security}
+\end{figure}
+We allow access by username and LDAP groups.
+The permissions can be scoped for individuals and groups.
+An example is removing Job delete permissions to prevent one user or group from deleting each other's jobs.
+
 \section{Anatomy of A Test}
 \label{sec:TestAnatomy}
-New software projects are required to be tested on our TDS and approved before deployment on Blue Waters and this is one of our key best practices. 
+New software projects are required to be tested on our test and development system (TDS) and approved before deployment on Blue Waters and this is one of our key best practices. 
  Once a test is deployed it is assigned to a specific Jenkins tab via the "Edit View" link associated with that tab. 
@@
 \subsection{ssh to a login host}
-There are several target ssh hosts which may be selected from our instance: the test rack JYC, the main system, and the new software deployment login node within the main system. 
+There are several target ssh hosts which may be selected from our instance: the TDS (JYC), the main system, and the new software deployment login node within the main system. 
  None of our tests run locally within the Jenkins VM.
@@
  As a best practice we also use the email notification as a method of tracking authorship and each test has an email owner even if notifications are disabled for the test.
+
+\section{SWTools Integration}
+\label{sec:SWToolsIntegration}
+\subsection{SWTools with Jenkins}
+%\begin{figure}[H]
+%\centering
+%\includegraphics[width=0.5\textwidth]{swtools-Jenkins}
+%\caption{ Use SWTools with Jenkins }
+%\label{fig:swtools-jenkins}
+%\end{figure}
+
+\subsection{SWTools with Lammps}
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{swtools-lammps}
+\caption{ SWTools with Lammps }
+\label{fig:swtools-lammps}
+\end{figure}
 
@@
 The initial display tabs in our Jenkins instance are used to group tests and we add tabs for special projects.
-For example we clone existing tests for evaluating a new software stack on our test login node.
-Our test rack has a separate set of tests from our production system and is used as our Jenkins development mule.
-The sustained petascale performance benchmarks are in their own tab because they run at scale and are only run on-demand by staff (not scheduled by Jenkins ).
+For example we clone existing tests for evaluating a new software stack on our test login node (h2ologin4).
+Our TDS (JYC) has a separate set of tests from our production system and is used as our Jenkins development mule.
+The sustained petascale performance benchmarks (SPP) are in their own tab because they run at scale and are only run on-demand by staff (not scheduled by Jenkins ).
 \begin{figure}[H]
@@
 Our production login nodes and the supercomputer have the latest PE installed as non default during initial testing and it can be loaded by modulefile selection.
-Our test login node (Bright Cluster Provisioned EsLogin) is utilized for testing new software stacks and changes to the login environment that are independent of our production resources.
+Our test login node is utilized for testing new software stacks and changes to the login environment that are independent of our production resources.
 Therefore Jenkins Projects tailored for each environment allow for regression testing of the current production as well as pre-production user-level environments.

### 2017-04-04 manuscript/manuscript.tex
Fixed author and my affiliation.

@@
 %
-\author{\IEEEauthorblockN{Timothy Bouvet, Reuben Budiardja, Galen Arnold}
-%xxxx\IEEEauthorrefmark{3} and
-%xxxx\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}National Institute for Computational Science\\
+
+\author{
+%\IEEEauthorblockN{Christian Y. Cardall, Eirik Endeve, \& Anthony Mezzacappa}
+\IEEEauthorblockN{Timothy Bouvet, Galen Arnold}
+\IEEEauthorblockA{
 National Center for Supercomputing Applications\\
 University of Illinois at Urbana-Champaign, 61801\\
-National Institute for Computational Sciences\\
-The University of Tennessee, Knoxville, TN 37996\\
-\{tbouvet@illinois.edu,reubendb@utk.edu,gwarnold@illinois.edu\}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Electrical Engineering and Computer Science Department\\University of Tennessee, Knoxville, TN 37996\\xx@eecs.utk.edu}
-%}
+tbouvet@illinois.edu, gwarnold@illinois.edu
+}
 
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
+\and
+
+\IEEEauthorblockN{Reuben D. Budiardja}
+\IEEEauthorblockA{
+National Center for Computational Sciences\\
+Oak Ridge National Laboratory, Oak Ridge, TN 37831\\
+reubendb@ornl.gov}
+}
 

### 2017-04-04 manuscript/manuscript.tex
Starting tweaking Anatomy section.

--- 2017-04-02 manuscript/manuscript.tex
@@
 
-\section{Anatomy of A Test}
+\section{Anatomy of A Test Application}
 \label{sec:TestAnatomy}
-New software projects are required to be tested on our TDS and approved before deployment on Blue Waters and this is one of our key best practices. 
- Once a test is deployed it is assigned to a specific Jenkins tab via the "Edit View" link associated with that tab. 
- Tests still in development reside in the "All" tab view until they have been peer reviewed by at least one other test developer.
-\subsection{test description}
-We require a description for each test to describe: what is tested, resources used by the test, intent of the test, and scheduling frequency.
-\subsection{limits log files}
-The Jenkins test VM filled to capacity after the first few weeks of intensive use and an influx of several new tests that output long source code build detail. 
- We retroactively modified all tests to limit the number of old build logs retained (max 50 for most tests).
+An application test is a Jenkins project. In this section we describe what a project typically consist of.
 
-\subsection{ssh to a login host}
+% New software projects are required to be tested on our TDS and approved before deployment on Blue Waters and this is one of our key best practices. 
+%  Once a test is deployed it is assigned to a specific Jenkins tab via the "Edit View" link associated with that tab. 
+%  Tests still in development reside in the "All" tab view until they have been peer reviewed by at least one other test developer.
+
+\subsection{Description}
+We require a description for each project to describe: what is tested, resources used by the test, intent of the test, and scheduling frequency.
+
+\subsection{Limiting Retained Build Log}
+The Jenkins VM filled to capacity after the first few weeks of intensive use and an influx of several new projects that output long source code build detail. 
+We retroactively modified all projects to limit the number of old build logs retained (maximum 50 for most projects).
+
+\subsection{SSH to a Login Host}
 There are several target ssh hosts which may be selected from our instance: the test rack JYC, the main system, and the new software deployment login node within the main system. 

### 2017-04-04 manuscript/manuscript.tex

--- 2017-04-04 manuscript/manuscript.tex
@@
 We show some use cases and describe our best practices for successfully using Jenkins as a user-level system-wide regression testing and monitoring framework for Blue Waters.
+
 \end{abstract}
@@
 
-\section{Authenticating with One-Time Password}
+\subsection{Authenticating with One-Time Password}
 
@@
 #-- OTP for Jenkins SSL connection
-DefineExternalAuth pwauth+session pipe \
+DefineExternalAuth pwauth+session pipe 
   /usr/local/bin/BasicAuthOTPSession.py
+>>>>>>> 5fc63821c62c4742a51b13b8301b3250eb23129c
 
@@
 
-\section{Authentication and Authorization}
-\label{sec:AuthenticationAuthorization}
+\subsection{Authorization and Access Control}
+\label{subsec:authorization}
 
-%\subsection{Security Considerations}
-%CUT THE NEXT TWO PARAGRAPHS AND DESCRIPTION OF CONFIG FILES OR REDUCE SINCE IT IS COVERED ABOVE --GALEN
-%Enabling Jenkins access to Blue Waters posed some unique security hurdles that we had to overcome. 
-%Blue Waters is an OTP only restricted access system. 
-%Jenkins has the ability to execute user-level commands on our login nodes. 
-%It also has some unfortunate default settings. 
-%The access control is set to "Jenkins' own user database," and the "Allow users to sign up" option is enabled, so if you don't have an account, you can create one by providing your name, e-mail and a password.
-%Additionally, there's an authorization option enabled which says "Logged-in users can do anything." So, once signed in, you have full admin access to the Jenkins system instance. 
-% This required us initially to test the deployment with our TDS. 
-%This resulted in the following requirement: restricted OTP access to the physical system hosting Jenkins. 
-%In addition, OTP only access to the Jenkins GUI command console must be contained within our IP space. 
-% The Jenkins GUI will also restrict the command console access to our Blue Waters LDAP server.
+Jenkins default authorization allows logged in (authenticated) users to have full control. 
+We wanted a more fine-grained access control to our instance and therefore selected the ''matrix-based security`` option (see Figure \ref{fig:jenkinsAuthorization}).
+Using this option we can limit what access individual users and groups have to our Jenkins instance.
+For example we restrict most users (other than admin users) from having the ''Job Delete`` permission to prevent one user or group from deleting each other's jobs.
 
-%\subsection{Configuration Choices}
-%The Jenkins instance was deployed on a vSphere managed VM running Centos 6.8.
-The VM allows restricted host-based ssh access from two secure OTP only administrative systems.
-The Jenkins GUI presented additional challenges.
-The Jenkins GUI is configured to log in as a standard user account with password-less access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM.
-We restrict access to the physical VM (bwjenkins) and the Jenkins GUI utilizing iptables, SSL and OTP.
-Jenkins is configured to listen on port 8080 by default and we restricted it to localhost only.
-A reverse proxy was configured to run Jenkins behind Apache HTTP Server and SSL for access to the administrative console.
-With this reverse proxy, apache accepts requests on port 80 and 443 of bwjenkins.ncsa.illinois.edu and forwards them to the Jenkins web server at localhost which is now firewall protected.
-Most of this configuration is in /etc/httpd/conf.d/ssl.conf.
-Anonymous access to the Jenkins GUI was allowed for limited read only view of test status and historical plots.
-The Anonymous access view is not restricted.
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\textwidth]{Configure-Global-Security}
+\caption{Jenkins fine-grained authorization.}
+\label{fig:jenkinsAuthorization}
+\end{figure}
 
-%\begin{lstlisting}
-%NOTE: Install mod_authnz_external Apache package
+We use the built-in LDAP plugin to query our LDAP server what group a user belongs to.
+This greatly simplifies managing the authorization since it can be done based on groups rather than just individual users. 
+The LDAP plugins gets the user information from the HTTP header passed by the reverse proxy set up. 
+Figure \ref{fig:LDAP-Jenkins} shows the screenshot of our LDAP configuration within Jenkins interface.
 
-%(Jenkins sever configuration file snippets below)
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
+\caption{Using LDAP with Jenkins.}
+\label{fig:LDAP-Jenkins}
+\end{figure}
 
-%/etc/ssh/sshd_config:
-%Match Host bwbh1.ncsa.illinois.edu,
-%bwbh2.ncsa.illinois.edu
-%HostbasedAuthentication yes
+Since Jenkins allows one to enter arbitrarily command to be executed on login nodes, we want to further mitigate security risk via firewall rules. 
+In our installation, we only allow IP address originating from our institution block to access the secure HTTP portion and authenticate to access Jenkins. 
+At NCSA, the non secure, read-only, HTTP portion is accessible from anywhere. 
+At NICS, this access is only allowed from the institution IP block only.
 
@@
 
-%/etc/httpd/conf.d/ssl.conf:
-% # -- The following sets ReverseProxy for Jenkins
-%ProxyRequests       Off
-%ProxyPreserveHost   On
-%AllowEncodedSlashes On
-%<Proxy *>
-%Order deny,allow
-%Allow from all
-%</Proxy>
-%ProxyPass       / http://localhost:8080/ nocanon
-%ProxyPassReverse / http://localhost:8080/
-%ProxyPassReverse / http://bwjenkins.ncsa.illinois.edu/
-%RequestHeader set X-Forwarded-Proto "https"
-%RequestHeader set X-Forwarded-Port "443"
-
-%\begin{lstlisting}
-% # -- OTP for Jenkins SSL connection
-%DefineExternalAuth pwauth+session pipe 
-%/usr/local/bin/pwauth+session
-%<LocationMatch / > 
-%AuthType Basic
-%AuthBasicProvider external
-%AuthName "NCSA RSA OTP login" 
-%AuthExternal pwauth+session
-%require valid-user  
-%RequestHeader unset "X-Forwarded-User"
-%RequestHeader set "X-Forwarded-User" (REMOTE_USER)
-%</LocationMatch>
- %
-%
-%/usr/local/bin/pwauth+session(OTP caching): 
-%https://github.com/reubendb/BasicAuthOTPSession
-%/blob/master/BasicAuthOTPSession.py#L1
-%
- % 
-%/etc/pam.d/pwauth (for OTP):
- %#%PAM-1.0
-%auth  required  /lib64/security/pam_securid.so
-%account  include  password-auth
-%\end{lstlisting}
-%/etc/sysconfig/jenkins (restrict to localhost):
-%JENKINS_PORT="8080"
-%JENKINS_LISTEN_ADDRESS=127.0.0.1
-%\end{lstlisting}
-\subsection{LDAP with Jenkins} 
-%To enable LDAP, the LDAP Plugin was installed.
-To configure, from the console view, select Manage Jenkins, then select Configure Global Security.
-In the Security Realm section select the Advanced...
-tab.
-Input your LDAP server name and root DN.
-Click the Test Button.
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
-\caption{ Use LDAP with Jenkins }
-\label{fig:LDAP-Jenkins}
-\end{figure}
-To enable LDAP, the LDAP Plugin was installed.
-To configure, from the console view, select Manage Jenkins, then select Configure Global Security.
-In the Security Realm section select the Advanced...
-tab.
-Input your LDAP server name and root DN.
-Click the Test Button.\\
-At first this failed because our LDAP is using a local CA.
-WARNING: Failed to search LDAP for username, 
-sun.security.provider.certpath.SunCertPathBuilderException:
-unable to find valid certification path to requested target\\
-\\
-We had to add our certificate to the keystore:
-/usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
-Enter keystore password: Trust this certificate? [no]:  yes\\
-Certificate was added to keystore
-
-\subsection{Configure Global Security}
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.5\textwidth]{Configure-Global-Security}
-\caption{ Configure Global Security }
-\label{fig:Configure-Global-Security}
-\end{figure}
-We allow access by username and LDAP groups.
-The permissions can be scoped for individuals and groups.
-An example is removing Job delete permissions to prevent one user or group from deleting each other's jobs.
-
-\section{Anatomy of A Test}
+\section{Anatomy of A Test Application}
 \label{sec:TestAnatomy}
@@
 There are several target ssh hosts which may be selected from our instance: the TDS (JYC), the main system, and the new software deployment login node within the main system.
+
  None of our tests run locally within the Jenkins VM.
@@
  As a best practice we also use the email notification as a method of tracking authorship and each test has an email owner even if notifications are disabled for the test.
-
-\section{SWTools Integration}
-\label{sec:SWToolsIntegration}
-\subsection{SWTools with Jenkins}
-%\begin{figure}[H]
-%\centering
-%\includegraphics[width=0.5\textwidth]{swtools-Jenkins}
-%\caption{ Use SWTools with Jenkins }
-%\label{fig:swtools-jenkins}
-%\end{figure}
-
-\subsection{SWTools with Lammps}
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.5\textwidth]{swtools-lammps}
-\caption{ SWTools with Lammps }
-\label{fig:swtools-lammps}
-\end{figure}
 

### 2017-04-04 manuscript/manuscript.tex
Working on FIXMEs.
Fixed paper outline in Introduction

@@
 The outline of this paper is as follows.
-[FIXME: WRITE PAPER OUTLINE AFTER COMPLETE DRAFT].
+In section \ref{sec:JenkinsConfiguration} we describe in details how we configure Jenkins for our deployment.
+This is followed by a brief description what an application test consist of in section \ref{sec:TestAnatomy}.
+Section \ref{sec:UseCases} shows some use cases and results from applications we have used to monitor our systems.
+We end the paper with concluding remarks in section \ref{sec:Conclusion}.
 
@@
 \section{Use Cases}
-\label{sec:results}
+\label{sec:UseCases}
 \subsection{IOR Lustre scratch test}
@@
 \section{Conclusion}
-\label{sec:conclusion}
+\label{sec:Conclusion}
 

### 2017-04-05 manuscript/manuscript.tex
Added references.

@@
 \usepackage{underscore}
+\usepackage{url}
 % correct bad hyphenation here
@@
 Our goal was to implement an automated solution for running these user-level regression tests to evaluate system usability and performance. 
-For this purpose we have chosen to use Jenkins\footnote{http://jenkins.io}.
+For this purpose we have chosen to use Jenkins \cite{jenkins}.
 
@@
 Each test application (i.e. ''project``) is then labeled to ensure that they only run on the appropriate node. 
-For example, we have used NAMD (FIXME: Need reference for NAMD) as an application test. 
+For example, we have used NAMD \cite{namd} as an application test. 
 We would create a Jenkins project called ''NAMD-Beacon`` and label it to run only on the ''beacon`` node. 
@@
 \subsubsection{Using SSH Plugins for Test Systems}
-The SSH plugin (FIXME: Need references) is another method for which one can access the HPC systems from Jenkins. 
+The SSH plugin \cite{JenkinsSSHPlugin} is another method for which one can access the HPC systems from Jenkins. 
 As the name implies, Jenkins projects with these type of build scripts simply SSH to the desired machine then execute the scripts there.
@@
 Second, we need to forward all HTTP requests to Jenkins, and also forward Jenkins responses back to the client. 
-This is accomplished using the module \texttt{mod_proxy} (FIXME: Add Reference) in Apache HTTP which allows it to act as a proxy / gateway. 
+This is accomplished using the module \texttt{mod_proxy} \cite{ApacheModProxy} in Apache HTTP which allows it to act as a proxy / gateway. 
 To enable this feature, the following stanza is added to the configuration file \texttt{/etc/httpd/conf.d/ssl.conf} inside the \texttt{<VirtualHost>} directive:
@@
 The default Jenkins authentication setup is also unfortunate, in which it allows anyone to self-register creating their own username and password\footnote{This is perhaps another artifact of Jenkins setup intended for intranet environment}.
-We wanted instead to use our One-Time Password (OTP) infrastructure with RSA SecurID (FIXME: Add references https://www.rsa.com/en-us/products/rsa-securid-suite, https://en.wikipedia.org/wiki/RSA_SecurID) token for authentication.
+We wanted instead to use our One-Time Password (OTP) infrastructure with RSA SecurID \cite{RSASecurID} token for authentication. 
 In this section we describe how we accomplished that.
 
-Our use of Apache HTTP Server as front-end allow us to use ''Basic Authentication`` (FIXME: Add Reference).
-Via \texttt{mod_authnz_external} module, one can use any external mechanism or program to authenticate.
+Our use of Apache HTTP Server as front-end allow us to use ''Basic Authentication`` \cite{ApacheBasicAuth}.
+Via \texttt{mod_authnz_external} module \cite{ApacheModAuthExt}, one can use any external mechanism or program to authenticate.
 One example of an authenticator is the ''pwauth`` authentication program. 
@@
 
-To accomplish this, we wrote a small python script called ''BasicAuthOTPSession`` [FIXME: Add Reference] as the authentication mechanism, wrapping the real authenticator (i.e.
+To accomplish this, we wrote a small python script for managing session with OTP \cite{BasicAuthOTPSession} as the authentication mechanism, wrapping the real authenticator (i.e.
 \texttt{pwauth} with PAM for RSA SecurID in our case).
-For the first time, it calls the real authenticator. 
+When this script is initially called, it uses a pre-defined back-end authenticator for authentication. 
 Once an authentication succeed, a session is created and the next request with the same credentials from the same IP address are deemed successful without going through the real authenticator. 
@@
 If there is no more request within that time, the session expires.
-When this happens, one has to authenticate again with the real authenticator.
+When this happens, one has to authenticate again with the back-end authenticator.
 
@@
   /usr/local/bin/BasicAuthOTPSession.py
->>>>>>> 5fc63821c62c4742a51b13b8301b3250eb23129c
 
@@
 
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-\IEEEtriggercmd{\enlargethispage{-2in}}
+% References
+\bibliographystyle{unsrt}
+\bibliography{references}
 
-% references section
-\section*{References}
-%[1] http://inca.sdsc.edu/ Inca Monitoring: periodic, automated, user-level cyberinfrastructure testing
-[1] https://jenkins.io/ Jenkins: open source automation server written in Java
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-
-%\begin{thebibliography}{9}
-
-%\bibliographystyle{IEEEtran}
-%\bibliographystyle{unsrt}
-%\bibliography{references}
-
-%\end{thebibliography}
-
-% that's all folks
 \end{document}

### 2017-04-05 manuscript/manuscript.tex
Added cross-ref for listing.

@@
 To achieve that, first we set the Jenkins web server to only listen to the \texttt{localhost} interface on port 8080, by setting the following variable in Jenkins configuration file \texttt{/etc/sysconfig/jenkins}:
-\begin{lstlisting}
+\begin{lstlisting}[captionpos=t,language=bash,label=lst:jenkinsConfig]
 #-- Restrict to only listen to localhost
@@
 
-\begin{lstlisting}
+\begin{lstlisting}[frame=b,captionpos=b,label=lst:reverseProxy,caption=Relevant configuration lines for setting up reverse proxy in Apache HTTP Server]
 ProxyRequests       Off
@@
 
-Figure {FIXME: CREATE FIGURE) illustrates the authentication mechanism we describe. 
-Most of the configuration is defined in the file \texttt{/etc/httpd/conf.d/ssl.conf}, immediately following listing [FIXME: CITE LISTING] inside the same \texttt{<VirtualHost>} directive:
+%Figure {FIXME: CREATE FIGURE) illustrates the authentication mechanism we describe. 
+Most of the configuration is defined in the file \texttt{/etc/httpd/conf.d/ssl.conf}, immediately following the stanza reproduced in listing \ref{lst:reverseProxy} inside the same \texttt{<VirtualHost>} directive:
 

### 2017-04-05 manuscript/manuscript.tex
Reworked conclusion. Very close to a good complete draft.

@@
 
-\section{Best Practices}
+\section{Conclusion}
+\label{sec:Conclusion}
+
+In this paper we have described our deployment of Jenkins automation server for user-level, application-based system monitoring and regression testing on large installation of HPC systems at NCSA and NICS.
+This monitoring system has proved to be useful in early detection of system issues.
+
+Another usefulness of this system is to anticipate issues related to software update. 
+We typically run the latest Programming Environment (PE) on our Test and Development System (TDS), while our production systems have the latest PE installed as non default. 
+During initial testing this newer PE can be loaded by modulefile selection.
+This setup allow us to use both the TDS and login node for testing the new software stacks and changes to the login environment without affecting the production environment.
+Jenkins projects tailored for each environment allow for regression testing of the current production as well as pre-production user-level environments with the new PE.
+
+In developing Jenkins projects for testing, we adhere to the following best practices: 
 \begin{itemize}
-\item Tests are developed on the JYC development rack and not assigned into a Jenkins tab until reviewed. 
+\item Tests are developed on the TDS and not assigned into a Jenkins tab until reviewed. 
 \item Email notification is enabled for most tests and the field is always populated with a test owner.
@@
 
-\section{Conclusion}
-\label{sec:Conclusion}
+In summary, our Jenkins-based system monitoring has allowed us to do:
 
-We typically run the latest Programming Environment (PE) on our TDS.
-Our production login nodes and the supercomputer have the latest PE installed as non default during initial testing and it can be loaded by modulefile selection.
-Our test login node is utilized for testing new software stacks and changes to the login environment that are independent of our production resources.
-Therefore Jenkins Projects tailored for each environment allow for regression testing of the current production as well as pre-production user-level environments.
+\begin{itemize}
 
-\subsection{reproducibility and regression testing}
-Jenkins provides the framework we need to maintain tests in a consistent fashion and track the results over time (logs and plots ).
+\item \textbf{Reproducibility and Regression Testing}: Jenkins provides the framework we need to maintain tests in a consistent fashion and track the results over time (logs and plots). 
 Tests typically are not changed so that we get apples-apples comparisons.
@@
 Reusable test components (watchdog scripts, plotting metrics) are employed to make construction of completely new tests straightforward.
-\subsection{rapid reaction}
+
+\item \textbf{Rapid Reaction}:
 The notification feature keeps test owners engaged in the testing activity of Jenkins and they are often our first responders to system issues.
 This results in a shorter reaction time when the system is not performing to expectations--staff are notified automatically when the user experience is impacted.
-\subsection{caveats}
-\subsubsection{transient errors}
-Transient errors with Jenkins sometimes occur--particularly with the Jenkins ssh subsystem.
+
+\end{itemize}
+
+In working with Jenkins test, we have found that it is useful to be aware of the following caveats:
+
+\begin{itemize}
+
+\item \textbf{Transient Errors}: Transient errors with Jenkins sometimes occur--particularly with the Jenkins ssh subsystem. 
 It's not unusual to get ssh failure rates of 1/100 which are completely transient (immediately running the test again manually clears the issue on the dashboard).
-\subsubsection{test scale and frequency}
-There is some subjectivity in the frequency and scale (resource utilization) of tests.
+
+\item \textbf{Test Scale and Frequency}: There is some subjectivity in the frequency and scale (resource utilization) of tests.
 Testing too often, too large, or some combination of the two may perturb the system such that other tests are impacted or create bottlenecks in the system for the real user community.
 This is the primary reason we require peer review for new tests.
+\end{itemize}
 

### 2017-04-05 manuscript/manuscript.tex
text cleanup

@@
 \begin{abstract}
-Monitoring and testing for regression of large scale systems such as the NCSA's Blue Waters supercompuer are challenging task. 
+Monitoring and testing for regression of large scale systems such as the NCSA's Blue Waters supercomputer are challenging tasks. 
 In this paper we describe the solution we came up with to perform those tasks. 
 Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance.
-Jenkins, an automation server software, was chosen for its versatility, large user base, and multitudes of plugins including collecting data and plotting test results over time. 
+Jenkins, an automation server software, was chosen for its versatility, large user base, and multitude of plugins including collecting data and plotting test results over time. 
 We describe our Jenkins deployment to launch and monitor jobs on remote HPC system, perform authentication with one-time password, and integrate with our LDAP server for its authorization. 
@@
 
-Monitoring large and complex high-performance computing systems have many challenges. 
-Layers and multiple versions of the software stack, system-level configurations, (parallel) file systems, diversity in user need and usage, and variable network traffic all interact to increase the system's complexity.
+Monitoring large and complex high-performance computing systems has many challenges. 
+Layers and multiple versions of the software stack, system-level configurations, (parallel) file systems, diversity in user needs and usage, and variable network traffic all interact to increase the system's complexity.
 Although there exist monitoring systems for each of these components, they often do not capture the behavior of the system in aggregate, which in fact is what users and their applications experience. 
@@
 
-Over time, either due to configuration and software changes or hardware aging, performance of such complex system may regress. 
+Over time, either due to configuration and software changes or hardware aging, performance of such a complex system may regress. 
 To identify and correct such regression, one must have some method to do regression testing of the system performance. 
@@
 
-In this paper we describe in detail our experience in using Jenkins to perform application-level regression testing on high-performance computing systems such as the Blue Water supercomputer at the National Center for Supercomputing Applications (NCSA), Darter and Beacon at the National Institute for Computational Sciences (NICS).
+In this paper we describe in detail our experience in using Jenkins to perform application-level regression testing on high-performance computing systems such as the Blue Water supercomputer at the National Center for Supercomputing Applications (NCSA), Darter, and Beacon at the National Institute for Computational Sciences (NICS).
 These systems are Cray XE, XK, XC, and CS series. 
 The outline of this paper is as follows.
-In section \ref{sec:JenkinsConfiguration} we describe in details how we configure Jenkins for our deployment.
+In section \ref{sec:JenkinsConfiguration} we describe in detail how we configure Jenkins for our deployment.
 This is followed by a brief description what an application test consist of in section \ref{sec:TestAnatomy}.
@@
 \subsubsection{Using Nodes for Test Systems}
-The original idea behind adding nodes is to allow Jenkins to scale with the workload it has to do. 
+The original idea behind adding nodes is to allow Jenkins to scale with its workload. 
 As projects are added, one can add nodes (i.e. more build machines) allowing Jenkins to build more projects concurrently. 
@@
 
-Jenkins nodes need to have a Java-based daemon (Jenkins' ''slave.jar``) to run which connects back to the master via a certain port (which is configurable). 
+Jenkins nodes need to have a Java-based daemon (Jenkins' ''slave.jar``) running which connects back to the master via a certain port (which is configurable). 
 This can be considered a drawback. 
@@
 Although Jenkins supplies its own authentication mechanism with its built-in user and password database, we feel that it is inadequate for securing our instance. 
-The default Jenkins authentication setup is also unfortunate, in which it allows anyone to self-register creating their own username and password\footnote{This is perhaps another artifact of Jenkins setup intended for intranet environment}.
+The default Jenkins authentication setup is unfortunate, in that it allows anyone to self-register creating their own username and password\footnote{This is perhaps another artifact of the Jenkins setup intended for intranet environment}.
 We wanted instead to use our One-Time Password (OTP) infrastructure with RSA SecurID \cite{RSASecurID} token for authentication. 
@@
 The session expires in a predefined amount of time. 
-A new request within that time renew the session. 
-If there is no more request within that time, the session expires.
+A new request within that time renews the session. 
+If there are no more requests within that time, the session expires.
 When this happens, one has to authenticate again with the back-end authenticator.
@@
 
-Since Jenkins allows one to enter arbitrarily command to be executed on login nodes, we want to further mitigate security risk via firewall rules. 
+Since Jenkins allows one to enter arbitrary commands to be executed on login nodes, we want to further mitigate security risk via firewall rules. 
 In our installation, we only allow IP address originating from our institution block to access the secure HTTP portion and authenticate to access Jenkins. 
@@
 \label{sec:TestAnatomy}
-New software projects are required to be tested on our test and development system (TDS) and approved before deployment on Blue Waters and this is one of our key best practices. 
+New software projects must be tested on our test and development system (TDS) and approved before deployment on Blue Waters and this is one of our key best practices. 
  Once a test is deployed it is assigned to a specific Jenkins tab via the "Edit View" link associated with that tab. 
@@
 
-Another usefulness of this system is to anticipate issues related to software update. 
+Another value of this system is to anticipate issues related to software updates. 
 We typically run the latest Programming Environment (PE) on our Test and Development System (TDS), while our production systems have the latest PE installed as non default. 
@@
 
-In summary, our Jenkins-based system monitoring has allowed us to do:
+In summary, our Jenkins-based system monitoring has enabled:
 
@@
 
-In working with Jenkins test, we have found that it is useful to be aware of the following caveats:
+In working with Jenkins tests, we have found that it is useful to be aware of the following caveats:
 

### 2017-04-11 manuscript/manuscript.tex
Minor tweaks.

--- 2017-04-05 manuscript/manuscript.tex
@@
 \label{sec:TestAnatomy}
-New software projects are required to be tested on our test and development system (TDS) and approved before deployment on Blue Waters and this is one of our key best practices. 
+New Jenkins projects (i.e.
+application tests) are required to be tested on our test and development system (TDS) and approved before deployment on Blue Waters.
+This is one of our key best practices.
 Once a test is deployed it is assigned to a specific Jenkins tab via the "Edit View" link associated with that tab.
- Tests still in development reside in the "All" tab view until they have been peer reviewed by at least one other test developer.
-\subsection{test description}
-We require a description for each test to describe: what is tested, resources used by the test, intent of the test, and scheduling frequency.
-\subsection{limits log files}
+Tests that are still in development reside in the "All" tab view until they have been peer reviewed by at least one other test developer.
+\subsection{Test Description}
+We require a description for each project to describe: what is tested, resources used by the test, intent of the test, and scheduling frequency.
+\subsection{Limits Log Files}
 The Jenkins test VM filled to capacity after the first few weeks of intensive use and an influx of several new tests that output long source code build detail.
@@
 
-\subsection{ssh to a login host}
+\subsection{SSH to a Login Host}
 There are several target ssh hosts which may be selected from our instance: the TDS (JYC), the main system, and the new software deployment login node within the main system.
@@
 
-In working with Jenkins test, we have found that it is useful to be aware of the following caveats:
+In working with Jenkins projects, we have found that it is useful to be aware of the following caveats:
 

### 2017-04-11 manuscript/manuscript.tex

--- 2017-04-05 manuscript/manuscript.tex
@@
 \subsection{ssh to a login host}
+
 There are several target ssh hosts which may be selected from our instance: the TDS (JYC), the main system, and the new software deployment login node within the main system.

### 2017-04-12 manuscript/manuscript.tex
Some rework of the Anatomy section, incorporating Galen's original write up.

@@
 \author{
-%\IEEEauthorblockN{Christian Y. Cardall, Eirik Endeve, \& Anthony Mezzacappa}
+  \IEEEauthorblockN{Reuben D. Budiardja}
+  \IEEEauthorblockA{
+    National Center for Computational Sciences\\
+    Oak Ridge National Laboratory, Oak Ridge, TN 37831\\
+    reubendb@ornl.gov}
+
+\and
+
   \IEEEauthorblockN{Timothy Bouvet, Galen Arnold}
@@
 
-\and
-
-\IEEEauthorblockN{Reuben D. Budiardja}
-\IEEEauthorblockA{
-National Center for Computational Sciences\\
-Oak Ridge National Laboratory, Oak Ridge, TN 37831\\
-reubendb@ornl.gov}
 }
@@
 \begin{IEEEkeywords}
-System-monitoring; Regression-testing; Application; Performance; Benchmarking
+System-monitoring; Regression-testing; Applications; Performance; Benchmarking
 \end{IEEEkeywords}
@@
 \label{sec:TestAnatomy}
-New software projects must be tested on our test and development system (TDS) and approved before deployment on Blue Waters and this is one of our key best practices. 
- Once a test is deployed it is assigned to a specific Jenkins tab via the "Edit View" link associated with that tab. 
- Tests still in development reside in the "All" tab view until they have been peer reviewed by at least one other test developer.
-\subsection{test description}
-We require a description for each test to describe: what is tested, resources used by the test, intent of the test, and scheduling frequency.
-\subsection{limits log files}
-The Jenkins test VM filled to capacity after the first few weeks of intensive use and an influx of several new tests that output long source code build detail. 
+In this section we briefly describe the primary elements of a test application. 
+A new test application (i.e. Jenkins job / project) must be tested on our test and development system (TDS) and approved before deployment on the user-facing production system (e.g. Blue Waters). 
+\footnote{We use the terms ''test application , ''test`` (for short), ''Jenkins project``, and ''Jenkins job`` interchangeably as they refer to the same thing.}
+This is one of our key best practices.
+
+Jenkins' dashboard by default shows the list of all Jenkins jobs under the ''All`` view tab. 
+One may create different ''views`` containing a list of selected projects. 
+In our case, we created several views to help us categorized our test applications.
+For example, once a test application is deployed on a production environment such as Blue Waters, it is assigned to the ''BlueWaters`` view. 
+This can be done by editing that view and add the selected applications to it.
+Tests that are still in development reside in the "All" tab view until they have been peer reviewed by at least one other test developer.
+
+\subsection{Name and Description}
+Beyond naming the Jenkins project, we require a description for each test to describe: what is tested, the resources used by the test, the intent of the test, and the scheduling frequency of the test.
+
+\subsection{Limiting Number of Builds Kept}
+The Jenkins VM filled to capacity after the first few weeks of intensive use and an influx of several new tests that output long source code build detail.
 We retroactively modified all tests to limit the number of old build logs retained (max 50 for most tests).
 
-\subsection{ssh to a login host}
+\subsection{Source Code Management}
+Jenkins is intended to be a continuous integration tool to assis software development, and therefore has in its core feature the ability to check out source code directly from a source code manager such as Subversion or Git (with plugin).
+For our purpose, most of our tests use a specified, static version of the application and therefore do not need this functionality.
 
-There are several target ssh hosts which may be selected from our instance: the TDS (JYC), the main system, and the new software deployment login node within the main system.
+We do have a small number of tests that automatically pulls from a repository containing SWTools2 scripts to build and test software. 
+SWTools2 is a software management tools we use to install center-provided applications and libraries.
+Having these tests in Jenkins is useful to make sure that we can still build the software correctly with any changes in the scripts or on the systems.
+In section \ref{sec:UseCases} we show some examples of these.
 
+\subsection{Build Triggers}
+In this part we specify how the job is triggered. 
+For most cases we do periodic builds with a time-based specification.
+
+\subsection{Build Commands}
+This is where we specify the (shell) commands to actually build (and run) our test application.
+This may include the actual commands to compile and link the executable, submitting jobs to the queue, and getting back and checking results.
+
+Where possible, we try to be as transparent with our test construction as possible. 
+We prefer explicit shell commands specified via Jenkins interface over running a script in the filesystem on the remote HPC system.
+Remote scripts are run with verbose mode or are displayed via \texttt{cat -n} to so that their output are captured by Jenkins console log.
+This makes it simpler for debugging when a test fails.
+
+As described in section \ref{sec:JenkinsConfiguration}, there are two mechanisms to run these commands on the actual HPC systems.
+Using Jenkins nodes mechanism, one would select ''Execute Shell`` as the build step and put the commands there.
+Using the ''SSH`` mechanism, one would select ''Execute shell script on remote host using ssh``.
+The former requires that one checks the ''restrict where this project can be run`` selection to specify the HPC system.
+With the latter, in our instance there are several target ssh hosts which may be selected: the TDS (JYC), the production system (Blue Waters), and the new software deployment login node within the main system.
 None of our tests run locally within the Jenkins VM.
-\subsection{run shell commands}
-A test is composed of shell command and where possible we try to be as transparent with our test construction as possible. 
-We prefer commands in the Jenkins configuration over running a script in the filesystem on the remote ssh target. 
-Scripts that are remote run with verbose mode or are displayed via "cat -n" to save output to the Jenkins console log and make for simpler debugging when a test fails.
-\subsubsection{test completes on login node}
-Some tests run only on the ssh login node and return more or less immediately. 
- Examples include tests for batch system functionality, ssh functionality, and filesystem functionality. 
+
+There are basically two kinds of tests:
+
+\subsubsection{Test Completes on the Login Node}
+Some tests run only on the login node and return more or less immediately.
+Examples include tests for batch system functionality, login / SSH functionality, and filesystem functionality.
 These tests are very similar in style to unit tests which target a limited set of functionality.
+
 \subsubsection{test is submitted to batch system}
 More comprehensive tests typically build and run an application or benchmark through the batch system.
- These tests exercise multiple aspects of the system: (filesystem, compilers and modules, high-speed network, external connectivity to the internet...). 
- They block to completion so that we do not overburden the batch system with tests. 
+These tests exercise multiple aspects of the system: (filesystem, compilers and modules, high-speed network, external connectivity to the internet, etc.).
+These tests are written such that they block to completion so that we do not overburden the batch system with tests.
 Unlike tests that run entirely on a login node, completion time can be highly variable depending on the queue depth and available backfill windows for the batch system.
-\subsection{post test actions}
-\subsubsection{scp files back to Jenkins host}
+
 Most comprehensive tests produce output that we use when debugging a failed test.
 They may also produce plot data.
- These files are copied back to the Jenkins host so that they can be viewed and/or incorporated into the plot feature of Jenkins.
-\subsubsection{plots}
-Successful tests save plot files and contribute a new data point to a plot. 
- The Jenkins server accumulates the data as rows in a spreadsheet (under /var/lib/jenkins/jobs/ ) and plots them via the "Plots" link for a test.
-\subsection{email notification}
+When using the ''SSH`` mechanism, these files are copied back to the Jenkins server so that they can be saved, viewed and/or incorporated into the plot feature of Jenkins.
+
+\subsection{Post-build Actions}
+
+After a test is run, arbitrary numbers of post-build actions can be specified. The following are some that we have used.
+
+\subsubsection{Plots}
+We installed Jenkins Plot plugin \cite{JenkinsPlotPlugin} so that successful tests can save plot files.
+The test needs to be written to generate a data point (e.g.
+performance value, timing, memory / IO bandwidth, etc.) to contribute to the plot.
+Under the hood, the Jenkins server accumulates the data as rows in a spreadsheet (in directory \texttt{/var/lib/jenkins/jobs/}) and plots them via the "Plots" link for a test.
+
+\subsubsection{Email Notification}
 When the state of a test changes, email notification is sent to the test owner.

### 2017-04-12 manuscript/manuscript.tex
Minor tweaks

@@
 
-\subsubsection{test is submitted to batch system}
+\subsubsection{Test Submitted to Batch System}
 More comprehensive tests typically build and run an application or benchmark through the batch system.

### 2017-04-12 manuscript/manuscript.tex
Changed to 1 line per sentence.
Tweaks on Use Cases: adding cross-ref and such.

@@
 
-After a test is run, arbitrary numbers of post-build actions can be specified. The following are some that we have used.
+After a test is run, arbitrary numbers of post-build actions can be specified. 
+The following are some that we have used.
 
@@
 We installed Jenkins Plot plugin \cite{JenkinsPlotPlugin} so that successful tests can save plot files. 
-The test needs to be written to generate a data point (e.g.
-performance value, timing, memory / IO bandwidth, etc.) to contribute to the plot.
+The test needs to be written to generate a data point (e.g. performance value, timing, memory / IO bandwidth, etc.) to contribute to the plot. 
 Under the hood, the Jenkins server accumulates the data as rows in a spreadsheet (in directory \texttt{/var/lib/jenkins/jobs/}) and plots them via the "Plots" link for a test.
@@
 \label{sec:UseCases}
-\subsection{IOR Lustre scratch test}
-We created Jenkins tests to periodically run the IOR MPI parallel i/o benchmark at modest scale and validate filesystem functionality and performance for the scratch filesystem. 
+\subsection{IOR for Lustre Scratch Test}
+We created Jenkins tests to periodically run the IOR MPI parallel I/O benchmark at modest scale and validate filesystem functionality and performance for the scratch filesystem. 
 The test is scaled to provide representative performance numbers for a typical small application while not creating performance issues with other jobs or the larger filesystem.
- One of our best practices is to provide a management level summary description for casual jenkins users who want to view the tests but do not need to understand the full Jenkins configuration and execution details.
+One of our best practices is to provide a management level summary description for casual Jenkins users who want to view the tests but do not need to understand the full Jenkins configuration and execution details.
 
@@
 \includegraphics[width=0.5\textwidth]{IOR-bluewaters-descr}
-\caption{ IOR description in jenkins }
+\caption{IOR description in Jenkins.}
 \label{fig:IOR-bluewaters-descr}
 \end{figure}
-Where possible, tests build from source and exercise multiple user-facing system components such as: git for external connectivity and modules to test defaults in the environment. 
- Where scripts on the remote SSH site are used, they are echoed and/or displayed with "cat -n" to make console output verbose and easy to debug in case of errors.
+Where possible, tests build from source and exercise multiple user-facing system components such as: Git for external connectivity and modules to test defaults in the environment. 
+Where scripts on the remote SSH site are used, they are echoed and/or displayed with \texttt{cat -n} to make console output verbose and easy to debug in case of errors.
 
@@
 The test synchronously blocks such that the next test will not start until the previous one has completed.
-We employ a watchdog script to monitor the batch queue and keep the test active until the system marks it as finished.
+We employ a watchdog script (see Listing \ref{lst:watchdog}) to monitor the batch queue and keep the test active until the system marks it as finished.
 This has the side effect of making the minimum test time an integer multiple of the sleep time in the watchdog script.
@@
 \includegraphics[width=0.5\textwidth]{IOR-watchdog-out}
-\caption{ IOR watchdog console output }
+\caption{ IOR watchdog console output.}
 \label{fig:IOR-watchdog-out}
 \end{figure}
-For tests that produce an interesting performance metric like IOR, we save that output to the file format expected by Jenkins and use plotting feature to produce plots. 
+For tests that produce an interesting performance metric like IOR, we save that output to the file format expected by Jenkins (see Listing \ref{lst:yvalue}) and use plotting feature to produce plots (Figure \ref{fig:IOR-plot}).
 \begin{lstlisting}[frame=tb,captionpos=t,language=bash,caption={sample YVALUE output file}, label=lst:yvalue]
@@
 \includegraphics[width=0.5\textwidth]{IOR-plot}
-\caption{ IOR plot view }
+\caption{IOR Plot View.}
 \label{fig:IOR-plot}
@@
 
-\subsection{mdtest Lustre tests}
+\subsection{mdtest Lustre Tests}
 The mdtest metadata test is run on the home and scratch filesystems to validate metadata server performance.
 The IOR and mdtest user-facing tests complement the fine-grained detail we are able to glean from the backed system-side counters in our OVIS database where we record details about individual server metrics and network traffic on the Cray Gemini fabric.
+Figure \ref{fig:mdtest-plot} plots the results of this test over certain period of time.
 \begin{figure}[H]
@@
 \includegraphics[width=0.5\textwidth]{mdtest-plot}
-\caption{ mdtest plot view }
+\caption{mdtest plot view }
 \label{fig:mdtest-plot}
@@
 An additional best practice is to enable E-mail Notifications to the test author and/or other interested parties.
-Setting notifications for unstable builds will trigger an E-mail every time the test state changes (from successful to failing and once again when successful ).
+Setting notifications for unstable builds will trigger an e-mail every time the test state changes (from successful to failing and once again when successful ).
+Figure \ref{fig:mdtest-config-email} shows screenshot of the email notification configuration for the mdtest test in Jenkins.
 \begin{figure}[H]
@@
 
-\subsection{filesystem dashboard}
-Our Jenkins instance is a source of information for a filesystem dashboard display we maintain in our wiki.
-The "http://" urls for the plot images are shown on the dashboard and provide a recent-time display of filesystem metrics from a user point of view.
-We add a Jenkins test to track response time of /bin/ls on the login nodes--a reasonable metric of metadata server health and also the most common problem reported by users when we are having filesystem issues.
+\subsection{Filesystem Dashboard}
+Our Jenkins instance is a source of information for a filesystem dashboard display we maintain in our wiki (Figure \ref{fig:wiki-dashboard}.
+The \texttt{http://} URLs for the plot images can be referred directly and are shown on the dashboard to provide a recent-time display of filesystem metrics from a user point of view.
+We add a Jenkins test to track response time of \texttt{/bin/ls} on the login nodes---a reasonable metric of metadata server health and also the most common problem reported by users when we are having filesystem issues.
 \begin{figure}[H]
@@
 
-\subsection{special projects}
-The initial display tabs in our Jenkins instance are used to group tests and we add tabs for special projects.
-For example we clone existing tests for evaluating a new software stack on our test login node (h2ologin4).
+\subsection{Special Projects}
+The initial display tabs (i.e.
+Jenkins ''Views``) in our Jenkins instance are used to group tests that are run periodically in production.
+We add separate ''Views`` for special projects.
+For example we clone existing tests for evaluating a new software stack on our test login node (''h2ologin4`` view).
 Our TDS (JYC) has a separate set of tests from our production system and is used as our Jenkins development mule.
-The sustained petascale performance benchmarks (SPP) are in their own tab because they run at scale and are only run on-demand by staff (not scheduled by Jenkins ).
+The sustained petascale performance benchmarks (SPP) are in their own tab because they run at scale and are only run on-demand by staff (i.e.
+not scheduled to run periodically by Jenkins}.
+Figure \ref{fig:tabs-display} illustrates our use of Jenkins views to organize our application tests.
 \begin{figure}[H]
@@
 \includegraphics[width=0.5\textwidth]{tabs-display}
-\caption{ tabs for project areas }
+\caption{Jenkins views (tabs) in our instance.}
 \label{fig:tabs-display}

### 2017-04-12 manuscript/manuscript.tex
Added reference, small addition in conclusion. Work in progress, won't build in latex.

@@
-\documentclass[10pt, conference, compsocconf]{IEEEtran}
+%\documentclass[10pt, conference, compsocconf]{IEEEtran}
+\documentclass{sig-alternate-05-2015}
 
@@
 \thispagestyle{plain}
+
+\setcopyright{licensedusgovmixed}
 
@@
 The sustained petascale performance benchmarks (SPP) are in their own tab because they run at scale and are only run on-demand by staff (i.e.
-not scheduled to run periodically by Jenkins}.
+not scheduled to run periodically by Jenkins).
 Figure \ref{fig:tabs-display} illustrates our use of Jenkins views to organize our application tests.
@@
 
+Due to our initial successful deployment of Jenkins as regression testing framework on NCSA and NICS resources,  it is currently being deployed on other resources including the CADES (Compute and Data Environment for Science) resources at the Oak Ridge National Laboratory.
+
 % use section* for acknowledgement

### 2017-04-12 manuscript/manuscript.tex
Added ORNL copyright notice, tweak acknowledment.

@@
-%\documentclass[10pt, conference, compsocconf]{IEEEtran}
-\documentclass{sig-alternate-05-2015}
+\documentclass[10pt, conference, compsocconf]{IEEEtran}
 
@@
 \pagestyle{plain}
+
+\newcommand\blfootnote[1]{%
+  \begingroup
+  \renewcommand\thefootnote{}\footnote{#1}%
+  \addtocounter{footnote}{-1}%
+  \endgroup
+}
+
 \begin{document}
@@
 
-\setcopyright{licensedusgovmixed}
-
 \begin{abstract}
@@
 \end{IEEEkeywords}
+
+\blfootnote{\textbf{Notice of copyright}: This manuscript has been authored by UT-Battelle, LLC under Contract No.
+DE-AC05-00OR22725 with the U.S.
+Department of Energy.
+The United States Government retains and the publisher, by accepting the article for publication, acknowledges that the United States Government retains a non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce the published form of this manuscript, or allow others to do so, for United States Government purposes.
+The Department of Energy will provide public access to these results of federally sponsored research in accordance with the DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}
 
@@
 \section*{Acknowledgment}
+We thank Gary Rogers at NICS for his help in setting up and testing OTP integration.
 This research used resources at the National Institute for Computational Sciences (NICS) and the National Center for Supercomputing Applications (NCSA), funded by the National Science Foundation (NSF).

### 2017-04-12 manuscript/manuscript.tex
Added NAMD test as example of SWTools integration. No further changes planned.

@@
 
+\subsection{NAMD Test}
+NAMD is one of many applications provided system-wide at NICS due to its high use.
+It is managed via SWTools2 \cite{SWTools2} such that build and test recipes are standardized.
+For the purpose of regression testing, we have written several glue scripts in SWTools to make it work seamlessly in Jenkins.
+Figure \ref{fig:NAMD-jenkins} shows screenshot of shell commands in Jenkins interface to build and test this application.
+The commands hide many of the complexities of building and executing the application behind SWTools recipes for NAMD.
+However, they are exactly the same commands used to build and test this application for provisioning to users \footnote{SWTools recipes for this case can be gleaned at  https://github.com/reubendb/SWTools-NICS-CI}.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{NAMD-Jenkins}
+\caption{Build commands for NAMD in Jenkins with SWTools2 integration.}
+\label{fig:NAMD-jenkins}
+\end{figure}
+
+For this application testing, we use a well known NAMD benchmark case ''ApoA1''.
+We collect performance data such as CPU time and memory usage and plot them over time (see Figure \ref{fig:NAMDPlot} for screenshot of the plots as seen in Jenkins interface).
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\textwidth]{NAMDPlot}
+\caption{Plots of NAMD test results in Jenkins.}
+\label{fig:NAMDPlot}
+\end{figure}
+
 \section{Conclusion}

### 2017-04-13 manuscript/manuscript.tex
Tweaks on conclusion; added some more acknowledment blurbs.

@@
 We describe our Jenkins deployment to launch and monitor jobs on remote HPC system, perform authentication with one-time password, and integrate with our LDAP server for its authorization. 
-We show some use cases and describe our best practices for successfully using Jenkins as a user-level system-wide regression testing and monitoring framework for Blue Waters.
+We show some use cases and describe our best practices for successfully using Jenkins as a user-level system-wide regression testing and monitoring framework for large supercomputer systems.
 
@@
 
-Due to our initial successful deployment of Jenkins as regression testing framework on NCSA and NICS resources,  it is currently being deployed on other resources including the CADES (Compute and Data Environment for Science) resources at the Oak Ridge National Laboratory.
+Our initial successful deployment of Jenkins as regression testing framework on NCSA and NICS resources leads to its being in deployment for other resources including the CADES (Compute and Data Environment for Science) resources at the Oak Ridge National Laboratory.
 
@@
 We thank Gary Rogers at NICS for his help in setting up and testing OTP integration.
-This research used resources at the National Institute for Computational Sciences (NICS) and the National Center for Supercomputing Applications (NCSA), funded by the National Science Foundation (NSF).
+This material is based upon work performed using computational resources at the National Institute for Computational Sciences (NICS) and the National Center for Supercomputing Applications (NCSA), funded by the National Science Foundation (NSF).
+NICS is supported by the University of Tennessee and Oak Ridge National Laboratory through the Joint Institute for Computational Sciences\footnote{http://www.jics.tennessee.edu}.
+A portion of this research used resources of the Oak Ridge Leadership Computing Facility at the Oak Ridge National Laboratory, which is supported by the Office of Science of the U.S.
+Department of Energy under Contract No.
+DE-AC05-00OR22725.
 

### 2017-04-30 manuscript/manuscript.tex
final edit and added references

@@
   \renewcommand\thefootnote{}\footnote{#1}%
-  \addtocounter{footnote}{-1}%
+  \addtocounter{footnote}{-1}%!TEX encoding = UTF-8 Unicode
   \endgroup
@@
 In this paper we describe the solution we came up with to perform those tasks. 
-Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance.
+Our goal was to find an automated solution for running user-level regression tests to evaluate system usability and performance.
 Jenkins, an automation server software, was chosen for its versatility, large user base, and multitude of plugins including collecting data and plotting test results over time. 
@@
 
-Monitoring large and complex high-performance computing systems has many challenges. 
-Layers and multiple versions of the software stack, system-level configurations, (parallel) file systems, diversity in user needs and usage, and variable network traffic all interact to increase the system's complexity.
+Monitoring large and complex high-performance computing systems have many challenges. 
+Layers and multiple versions of the software stack, system-level configurations, (parallel) file systems, diversity in user need and usage, and variable network traffic all interact to increase the system's complexity.
 Although there exist monitoring systems for each of these components, they often do not capture the behavior of the system in aggregate, which in fact is what users and their applications experience. 
@@
 
-In this paper we describe in detail our experience in using Jenkins to perform application-level regression testing on high-performance computing systems such as the Blue Water supercomputer at the National Center for Supercomputing Applications (NCSA), Darter, and Beacon at the National Institute for Computational Sciences (NICS).
+In this paper we describe in detail our experience in using Jenkins to perform application-level regression testing on high-performance computing systems such as the Blue Waters supercomputer at the National Center for Supercomputing Applications (NCSA) \cite{NCSA}, Darter, and Beacon at the National Institute for Computational Sciences (NICS) \cite{NICS}.
 These systems are Cray XE, XK, XC, and CS series. 
@@
 In section \ref{sec:JenkinsConfiguration} we describe in detail how we configure Jenkins for our deployment.
-This is followed by a brief description what an application test consist of in section \ref{sec:TestAnatomy}.
+This is followed by a brief description of application test structure in section \ref{sec:TestAnatomy}.
 Section \ref{sec:UseCases} shows some use cases and results from applications we have used to monitor our systems.
@@
 We used the RPM package to install Jenkins on a CentOS virtual machine (VM). 
-Jenkins comes with its own web server so that managing and accessing Jenkins can be done via any web browser (in the next section we discuss using Apache HTTP Server in front of Jenkin's for better security).
+Jenkins comes with its own web server so that managing and accessing Jenkins can be done via any web browser (in the next section we discuss using Apache HTTP Server in front of Jenkins for better security).
 Typically Jenkins's web server listens on port 8080, but this is configurable.
@@
 The NCSA login node's \texttt{/etc/ssh/sshd_config} was modified to allow ''Public Key Authentication`` from the Jenkins VM unique IP address. 
-We created an NCSA user called ''bwjenkins`` with standard user privilege. 
+We created a NCSA user called ''bwjenkins`` with standard user privilege. 
 Pairs of SSH keys with passphrase were generated on the Jenkins VM with their public keys deployed on the appropriate login nodes in the bwjenkins user account to allow passwordless login. 
 The SSH plugins allow one to manage which key (and passphrase) to use with which system. 
-The keys on the Jenkins VM are located under the Jenkins home directory (by default \texttt{/var/lib/jenkins/.ssh}. 
+The keys on the Jenkins VM are located under the Jenkins home directory (by default) \texttt{/var/lib/jenkins/.ssh}. 
 Although this configuration can be somewhat tedious, when complete, Jenkins will be able to run scripts on the intended HPC systems via SSH. 
@@
 The remote systems' workspaces are out of the reach of Jenkins. 
-This drawback also prevents one to easily allow concurrent builds of the same project.
+This drawback also prevents one from easily allowing concurrent builds of the same project.
 
@@
 At NCSA, the non secure, read-only, HTTP portion is accessible from anywhere. 
-At NICS, this access is only allowed from the institution IP block only.
+At NICS, this access is only allowed from the institution IP block.
 
@@
 We do have a small number of tests that automatically pulls from a repository containing SWTools2 scripts to build and test software. 
-SWTools2 is a software management tools we use to install center-provided applications and libraries.
+SWTools2 is a software management tool we use to install center-provided applications and libraries.
 Having these tests in Jenkins is useful to make sure that we can still build the software correctly with any changes in the scripts or on the systems.
@@
 This is where we specify the (shell) commands to actually build (and run) our test application. 
-This may include the actual commands to compile and link the executable, submitting jobs to the queue, and getting back and checking results.
+This may include the actual commands to compile and link the executable, submitting jobs to the queue, retrieving artifacts and checking results.
 
@@
 We prefer explicit shell commands specified via Jenkins interface over running a script in the filesystem on the remote HPC system. 
-Remote scripts are run with verbose mode or are displayed via \texttt{cat -n} to so that their output are captured by Jenkins console log. 
+Remote scripts are run with verbose mode or are displayed via \texttt{cat -n} so that their outputs are captured by the Jenkins project console log. 
 This makes it simpler for debugging when a test fails.
@@
 The former requires that one checks the ''restrict where this project can be run`` selection to specify the HPC system. 
-With the latter, in our instance there are several target ssh hosts which may be selected: the TDS (JYC), the production system (Blue Waters), and the new software deployment login node within the main system.
+With the latter, in our instance there are several target ssh hosts which may be selected: the TDS (JYC), the production system (Blue Waters), and the new software deployment login node (H2ologin4) within the main system.
 None of our tests run locally within the Jenkins VM.
@@
 The test is scaled to provide representative performance numbers for a typical small application while not creating performance issues with other jobs or the larger filesystem.
-One of our best practices is to provide a management level summary description for casual Jenkins users who want to view the tests but do not need to understand the full Jenkins configuration and execution details.
+One of our best practices is to provide a management level summary description (see Figure \ref{fig:IOR-bluewaters-descr}) for casual Jenkins users who want to view the tests but do not need to understand the full Jenkins configuration and execution details.
 
@@
 The mdtest metadata test is run on the home and scratch filesystems to validate metadata server performance.
-The IOR and mdtest user-facing tests complement the fine-grained detail we are able to glean from the backed system-side counters in our OVIS database where we record details about individual server metrics and network traffic on the Cray Gemini fabric.
-Figure \ref{fig:mdtest-plot} plots the results of this test over certain period of time.
+The IOR and mdtest user-facing tests complement the fine-grained detail we are able to glean from the backend system-side counters in our OVIS \cite{OVIS} database where we record details about individual server metrics and network traffic on the Cray Gemini fabric.
+Figure \ref{fig:mdtest-plot} plots the results of this test over a certain period of time.
 \begin{figure}[H]
@@
 An additional best practice is to enable E-mail Notifications to the test author and/or other interested parties.
-Setting notifications for unstable builds will trigger an e-mail every time the test state changes (from successful to failing and once again when successful ).
+Setting notifications for unstable builds will trigger an e-mail every time the test state changes (from successful to failing and once again when successful).
 Figure \ref{fig:mdtest-config-email} shows screenshot of the email notification configuration for the mdtest test in Jenkins.
@@
 \subsection{Filesystem Dashboard}
-Our Jenkins instance is a source of information for a filesystem dashboard display we maintain in our wiki (Figure \ref{fig:wiki-dashboard}.
+Our Jenkins instance is a source of information for a filesystem dashboard display we maintain in our wiki (Figure \ref{fig:wiki-dashboard}).
 The \texttt{http://} URLs for the plot images can be referred directly and are shown on the dashboard to provide a recent-time display of filesystem metrics from a user point of view.
@@
 We add separate ''Views`` for special projects.
-For example we clone existing tests for evaluating a new software stack on our test login node (''h2ologin4`` view).
+For example we clone existing tests for evaluating a new software stack on our test login node (''H2ologin4`` view).
 Our TDS (JYC) has a separate set of tests from our production system and is used as our Jenkins development mule.
@@
 For the purpose of regression testing, we have written several glue scripts in SWTools to make it work seamlessly in Jenkins.
-Figure \ref{fig:NAMD-jenkins} shows screenshot of shell commands in Jenkins interface to build and test this application.
+Figure \ref{fig:NAMD-jenkins} shows a screenshot of shell commands in the Jenkins interface to build and test this application.
 The commands hide many of the complexities of building and executing the application behind SWTools recipes for NAMD.
@@
 
-In this paper we have described our deployment of Jenkins automation server for user-level, application-based system monitoring and regression testing on large installation of HPC systems at NCSA and NICS.
+In this paper we have described our deployment of Jenkins automation server for user-level, application-based system monitoring and regression testing on large installations of HPC systems at NCSA and NICS.
 This monitoring system has proved to be useful in early detection of system issues.

### 2017-05-09 manuscript/manuscript.tex
Updated with CCPE footnote.

@@
 The United States Government retains and the publisher, by accepting the article for publication, acknowledges that the United States Government retains a non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce the published form of this manuscript, or allow others to do so, for United States Government purposes.
-The Department of Energy will provide public access to these results of federally sponsored research in accordance with the DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}
+The Department of Energy will provide public access to these results of federally sponsored research in accordance with the DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).
+
+This paper has been submitted as an article in a special issue of Concurrency and Computation Practice and Experience on the Cray User Group 2017.}
 

### 2017-05-19 manuscript/manuscript.tex
corrected typos on page2 and 5

@@
 In our case, this is not what we want. 
-In fact, our applications will be built on the HPC system on which we intent to run the tests (typically on the login nodes), and will be run on the compute nodes of the HPC system (i.e.
+In fact, our applications will be built on the HPC system on which we intend to run the tests (typically on the login nodes), and will be run on the compute nodes of the HPC system (i.e.
 via batch job submission to the job queueing system).
@@
 \subsection{Source Code Management}
-Jenkins is intended to be a continuous integration tool to assis software development, and therefore has in its core feature the ability to check out source code directly from a source code manager such as Subversion or Git (with plugin).
+Jenkins is intended to be a continuous integration tool to help with software development, and therefore has in its core features the ability to check out source code directly from a source code manager such as Subversion or Git (with plugin).
 For our purpose, most of our tests use a specified, static version of the application and therefore do not need this functionality.

### 2017-06-01 manuscript_ccpe/manuscript.tex
Reformatted for CCPE submission.

--- 2017-05-19 manuscript/manuscript.tex
@@
-\documentclass[10pt, conference, compsocconf]{IEEEtran}
+\documentclass[AMA]{WileyNJD-v1}
+
+\articletype{CUG2017 Conference Proceeding}
 
 \usepackage{graphicx}
-\usepackage{algorithmic,listings}
+%\usepackage{algorithmic,listings}
+\usepackage{listings}
 \lstset{language=C,basicstyle=\small\ttfamily, basewidth=0.51em}
@@
 \usepackage{url}
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
 
 \graphicspath{{figures/}}
-\pagestyle{plain}
 
-\newcommand\blfootnote[1]{%
-  \begingroup
-  \renewcommand\thefootnote{}\footnote{#1}%
-  \addtocounter{footnote}{-1}%!TEX encoding = UTF-8 Unicode
-  \endgroup
-}
+\raggedbottom
 
@@
 
-\title{Application-Level Regression Testing Framework using Jenkins}
+\title{Application-Level Regression Testing Framework using Jenkins\protect\thanks{\textbf{Notice of copyright}: This manuscript has been authored by UT-Battelle, LLC under Contract No.
+DE-AC05-00OR22725 with the U.S.
+Department of Energy.
+The United States Government retains and the publisher, by accepting the article for publication, acknowledges that the United States Government retains a non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce the published form of this manuscript, or allow others to do so, for United States Government purposes.
+The Department of Energy will provide public access to these results of federally sponsored research in accordance with the DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}}
 
-% author names and affiliations 
-% use a multiple column layout for up to two different
-% affiliations
+\author[1]{Reuben D. Budiardja*}
 
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
+\author[2]{Timothy Bouvet}
 
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-%
+\author[2]{Galen Arnold}
 
-\author{
-  \IEEEauthorblockN{Reuben D. Budiardja}
-  \IEEEauthorblockA{
-    National Center for Computational Sciences\\
-    Oak Ridge National Laboratory, Oak Ridge, TN 37831\\
-    reubendb@ornl.gov}
+\authormark{Budiardja \textsc{et al}}
 
-\and
+\address[1]{\orgdiv{National Center for Computational Sciences}, \orgname{Oak Ridge National Laboratory}, \orgaddress{\state{Oak Ridge, TN 37831}, \country{USA}}}
 
-  \IEEEauthorblockN{Timothy Bouvet, Galen Arnold}
-  \IEEEauthorblockA{
-    National Center for Supercomputing Applications\\
-    University of Illinois at Urbana-Champaign, 61801\\
-    tbouvet@illinois.edu, gwarnold@illinois.edu
-  }
+\address[2]{\orgdiv{National Center for Supercomputing Applications}, \orgname{University of Illinois at Urbana-Champaign}, \orgaddress{\state{IL 61801}, \country{USA}}}
 
-}
+\corres{*Reuben D. Budiardja, Oak Ridge National Laboratory, One Bethel Valley Road, P.O. Box 2008, MS-6008, Oak Ridge, TN 37831-6008 \email{reubendb@ornl.gov}}
 
-% make the title area
-\maketitle
-\thispagestyle{plain}
-
-\begin{abstract}
-Monitoring and testing for regression of large scale systems such as the NCSA's Blue Waters supercomputer are challenging tasks. 
+\abstract[Summary]{Monitoring and testing for regression of large scale systems such as the NCSA's Blue Waters supercomputer are challenging tasks. 
 In this paper we describe the solution we came up with to perform those tasks. 
@@
 We describe our Jenkins deployment to launch and monitor jobs on remote HPC system, perform authentication with one-time password, and integrate with our LDAP server for its authorization. 
-We show some use cases and describe our best practices for successfully using Jenkins as a user-level system-wide regression testing and monitoring framework for large supercomputer systems.
+We show some use cases and describe our best practices for successfully using Jenkins as a user-level system-wide regression testing and monitoring framework for large supercomputer systems.}
 
-\end{abstract}
+\keywords{System-monitoring; Regression-testing; Applications; Performance; Benchmarking}
 
-\begin{IEEEkeywords}
-System-monitoring; Regression-testing; Applications; Performance; Benchmarking
-\end{IEEEkeywords}
-
-\blfootnote{\textbf{Notice of copyright}: This manuscript has been authored by UT-Battelle, LLC under Contract No.
-DE-AC05-00OR22725 with the U.S.
-Department of Energy.
-The United States Government retains and the publisher, by accepting the article for publication, acknowledges that the United States Government retains a non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce the published form of this manuscript, or allow others to do so, for United States Government purposes.
-The Department of Energy will provide public access to these results of federally sponsored research in accordance with the DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).
-
-This paper has been submitted as an article in a special issue of Concurrency and Computation Practice and Experience on the Cray User Group 2017.}
+\maketitle
 

### 2017-06-01 manuscript_ccpe/manuscript.tex
Updated BW acknowledment.

@@
 \section*{Acknowledgment}
-We thank Gary Rogers at NICS for his help in setting up and testing OTP integration.
-This material is based upon work performed using computational resources at the National Institute for Computational Sciences (NICS) and the National Center for Supercomputing Applications (NCSA), funded by the National Science Foundation (NSF).
+This material is based upon work performed using computational resources at the National Institute for Computational Sciences (NICS).
 NICS is supported by the University of Tennessee and Oak Ridge National Laboratory through the Joint Institute for Computational Sciences\footnote{http://www.jics.tennessee.edu}.
-A portion of this research used resources of the Oak Ridge Leadership Computing Facility at the Oak Ridge National Laboratory, which is supported by the Office of Science of the U.S.
+This material is part of the Blue Waters sustained-petascale computing project, which is supported by the National Science Foundation (awards OCI-0725070 and ACI-1238993) and the state of Illinois.
+Blue Waters is a joint effort of the University of Illinois at Urbana-Champaign and its National Center for Supercomputing Applications.
+A portion of this work used resources of the Oak Ridge Leadership Computing Facility at the Oak Ridge National Laboratory, which is supported by the Office of Science of the U.S.
 Department of Energy under Contract No.

### 2017-08-30 manuscript_ccpe/manuscript.tex
Added reference to address comment on evaluation of other tools.
Added ref for IOR config script and watchdog in the text.

@@
 Our goal was to implement an automated solution for running these user-level regression tests to evaluate system usability and performance. 
-For this purpose we have chosen to use Jenkins \cite{jenkins}.
+For this purpose we have chosen to use Jenkins \cite{jenkins}. (For an evaluation of other tools that may be used for this purpose, see \cite{VergaraLarrea}.)
 
@@
 \end{figure}
-The IOR test is set to run as scheduled by Jenkins with a best-effort through our batch system.
+The IOR test is set to run as scheduled by Jenkins with a best-effort through our batch system. Figure \ref{fig:IOR-configuration-sample} shows sample configuration script for this test. 
 The test synchronously blocks such that the next test will not start until the previous one has completed.
-We employ a watchdog script (see Listing \ref{lst:watchdog}) to monitor the batch queue and keep the test active until the system marks it as finished.
+We employ a watchdog script (see Listing \ref{lst:watchdog} and its output \ref{fig:IOR-watchdog-out}) to monitor the batch queue and keep the test active until the system marks it as finished.
 This has the side effect of making the minimum test time an integer multiple of the sleep time in the watchdog script.
